---
title: "Sphk1_Project"
author: "Sedat Kacar"
date: '`r Sys.Date()`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

library(Seurat)
library(dplyr)
library(ggplot2)
```


```{r}
Vpc1 <- Read10X_h5(file = "C:/Users/skacar/OneDrive - Indiana University/PULMONARY POST DOC/___SPHK1_PROJECT____/barcodes_sphk1/filtered_feature_bc_matrix_vpc1.h5")
Vpc2 <- Read10X_h5(file = "C:/Users/skacar/OneDrive - Indiana University/PULMONARY POST DOC/___SPHK1_PROJECT____/barcodes_sphk1/filtered_feature_bc_matrix_vpc2.h5")
Vpc3 <- Read10X_h5(file = "C:/Users/skacar/OneDrive - Indiana University/PULMONARY POST DOC/___SPHK1_PROJECT____/barcodes_sphk1/filtered_feature_bc_matrix_vpc3.h5")
Vpc4 <- Read10X_h5(file = "C:/Users/skacar/OneDrive - Indiana University/PULMONARY POST DOC/___SPHK1_PROJECT____/barcodes_sphk1/filtered_feature_bc_matrix_vpc4.h5")

```


```{r}
Vpc1 <- CreateSeuratObject(Vpc1,
                                    min.cells=3,
                                    min.features = 100)

Vpc2 <- CreateSeuratObject(Vpc2,
                                    min.cells=3,
                                    min.features = 100)

Vpc3 <- CreateSeuratObject(Vpc3,
                                    min.cells=3,
                                    min.features = 100)
Vpc4 <- CreateSeuratObject(Vpc4,
                                    min.cells=3,
                                    min.features = 100)

```


```{r}

for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
  obj <- get(i)
  obj[["percent.mt"]] <- PercentageFeatureSet(obj, pattern = "^mt-")
  assign(i, obj)
}

```



```{r, fig.height=15, fig.width=10}
library(ggplot2)

for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
obj <- get(i)
# Plot features vs counts
p1 <- FeatureScatter(obj, feature1 = "nCount_RNA", feature2 = "nFeature_RNA") + geom_hline(yintercept = 5000, linetype = "dashed", color = "red", size = 1.5) + geom_vline(xintercept = c(800, 17000), linetype = "dashed", color = "red", size = 1.5)  + theme(legend.position = "none") + ggtitle(i)
# Display the combined plot
p2 <- VlnPlot(obj, features = "percent.mt") + geom_hline(yintercept = 10, linetype = "dashed", color = "red", size = 1.5) + theme(legend.position = "none") + ggtitle(i)
print(p1/p2)
}

```



```{r}
for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
  obj <- get(i)
obj <- subset(obj, subset = nFeature_RNA > 100 & nFeature_RNA < 5000 & nCount_RNA < 17000 & nCount_RNA > 800 & percent.mt < 10)
assign(i, obj)
}
```


```{r}
for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
    obj <- get(i)
obj <- NormalizeData(obj)
obj <- FindVariableFeatures(obj, selection.method = "vst", nfeatures = 2000)
assign(i, obj)
}
```


```{r}
for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
    obj <- get(i)
obj$orig.ident <- i
assign(i, obj)
}
```


```{r}

anchors <- FindIntegrationAnchors(object.list = list(Vpc1, Vpc2, Vpc3, Vpc4))

```
```{r}
combined <- IntegrateData(anchorset = anchors)

```
#Vpc1
```{r, fig.height=12, fig.width=10}

for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
    obj <- get(i)
obj <- ScaleData(obj)
obj <- RunPCA(obj, npcs = 50)
obj <- RunUMAP(obj, dims = 1:50)
obj <- FindNeighbors(obj, dims = 1:30)
obj <- FindClusters(obj, resolution = 0.30)
assign(i, obj)
}




Vpc1 <- ScaleData(Vpc1)

Vpc1 <- RunPCA(Vpc1, npcs = 50)
Vpc1 <- RunUMAP(Vpc1, dims = 1:50)
Vpc1 <- FindNeighbors(Vpc1, dims = 1:30)
Vpc1 <- FindClusters(Vpc1, resolution = 0.30)
DimPlot(Vpc1, label = T) + theme(legend.position = "bottom")
DimPlot(Vpc1, label = T, split.by = "orig.ident") + theme(legend.position = "bottom")


```

#RNA

```{r, fig.height=12, fig.width=10}

RNA_SPHK1 <- combined
rm(combined)
RNA_SPHK1 <- ScaleData(RNA_SPHK1)

RNA_SPHK1 <- RunPCA(RNA_SPHK1, npcs = 50)
RNA_SPHK1 <- RunUMAP(RNA_SPHK1, dims = 1:50)
RNA_SPHK1 <- FindNeighbors(RNA_SPHK1, dims = 1:30)
RNA_SPHK1 <- FindClusters(RNA_SPHK1, resolution = 0.30)
DimPlot(RNA_SPHK1, label = T) + theme(legend.position = "bottom")
DimPlot(RNA_SPHK1, label = T, split.by = "orig.ident") + theme(legend.position = "bottom")




library(gridExtra)
library(ggplot2) 
# Open a PNG device to save the output as a high-resolution image (300 dpi)
png("RNA_seurat_SPHK1_0.30_new.png", width = 9, height = 9, units = "in", res = 300)

# Arrange and save all plots in a grid with 3 columns
DimPlot(RNA_SPHK1, label = T) + theme(legend.position = "bottom") + ggtitle("RNA SPHK1")

# Close the graphics device
dev.off()


getwd()

```


#SC TRANSFORM

```{r}

for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
    obj <- get(i)
obj <- SCTransform(obj, vars.to.regress = "percent.mt", verbose = FALSE)
assign(i, obj)
}
```





```{r}
anchors <- FindIntegrationAnchors(object.list = list(Vpc1, Vpc2, Vpc3, Vpc4))
combined <- IntegrateData(anchorset = anchors)

```
#SCT Integrated

```{r, fig.height=12, fig.width=10}

SCT_SPHK1 <- combined
rm(combined)
SCT_SPHK1 <- ScaleData(SCT_SPHK1)

SCT_SPHK1 <- RunPCA(SCT_SPHK1, npcs = 50)
SCT_SPHK1 <- RunUMAP(SCT_SPHK1, dims = 1:50)
SCT_SPHK1 <- FindNeighbors(SCT_SPHK1, dims = 1:30)
SCT_SPHK1 <- FindClusters(SCT_SPHK1, resolution = 0.30)
DimPlot(SCT_SPHK1, label = T) + theme(legend.position = "bottom")
DimPlot(SCT_SPHK1, label = T, split.by = "orig.ident") + theme(legend.position = "bottom")




library(gridExtra)
library(ggplot2) 
# Open a PNG device to save the output as a high-resolution image (300 dpi)
png("SCT_seurat_SPHK1_0.30.png", width = 9, height = 9, units = "in", res = 300)

# Arrange and save all plots in a grid with 3 columns
DimPlot(SCT_SPHK1, label = T) + theme(legend.position = "bottom") + ggtitle("SCT SPHK1")

# Close the graphics device
dev.off()


getwd()



#Constructing the group name with ifelse
SCT_SPHK1$group <- ifelse(grepl("_1$", colnames(SCT_SPHK1)), "WT Normoxia",
                               ifelse(grepl("_2$", colnames(SCT_SPHK1)), "WT Hypoxia",
                                      ifelse(grepl("_3$", colnames(SCT_SPHK1)), "SPHK1 Normoxia", "SPHK1 Hypoxia")))

rm(list = ls())

```

#TRANSFER DATA WITH PARSE

```{r, fig.height=10, fig.width=10}
#BISMILLAHIRRAHMANIRRAHIM

Parsall_comb$general_group_nounk
Parsall_comb$general_group_w_na

Vpc1 <- RNA_SPHK1_list[1]$Vpc1
Vpc2 <- RNA_SPHK1_list[2]$Vpc2
Vpc3 <- RNA_SPHK1_list[3]$Vpc3
Vpc4 <- RNA_SPHK1_list[4]$Vpc4

for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
    obj <- get(i)
    anchors <- FindTransferAnchors(
      reference = Parsall_comb,         # Reference Seurat object (with known T cell labels)
  query = obj,                 # Query Seurat object (to which we want to transfer labels)
  normalization.method = "LogNormalize",       # Normalization method (use "SCT" if you did SCTransform or "SCT")
  reference.assay = "RNA",            # Assay in the reference Seurat object (usually "RNA" for raw or normalized counts)
  query.assay = "RNA",                # Assay in the query Seurat object
  dims = 1:30)
    #2- Second Tranfer labels
    Bis_TRANSITIVE_Elh <- TransferData(anchorset = anchors,
                             refdata = Parsall_comb$general_group_nounk,
                             dims = 1:30
                             )
    obj$general_group_nounk <- Bis_TRANSITIVE_Elh$predicted.id
    assign(i, obj)
}



for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
    obj <- get(i)
    anchors <- FindTransferAnchors(
      reference = Parsall_comb,         # Reference Seurat object (with known T cell labels)
  query = obj,                 # Query Seurat object (to which we want to transfer labels)
  normalization.method = "LogNormalize",       # Normalization method (use "SCT" if you did SCTransform or "SCT")
  reference.assay = "RNA",            # Assay in the reference Seurat object (usually "RNA" for raw or normalized counts)
  query.assay = "RNA",                # Assay in the query Seurat object
  dims = 1:30)
    #2- Second Tranfer labels
    Bis_TRANSITIVE_Elh <- TransferData(anchorset = anchors,
                             refdata = Parsall_comb$general_group_w_na,
                             dims = 1:30
                             )
    obj$general_group_w_na <- Bis_TRANSITIVE_Elh$predicted.id
    assign(i, obj)
    Bis_TRANSITIVE_Elh <- TransferData(anchorset = anchors,
                             refdata = Parsall_comb$general_group_nounk,
                             dims = 1:30
                             )
    obj$general_group_nounk <- Bis_TRANSITIVE_Elh$predicted.id
    assign(i, obj)
}






for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
      obj <- get(i)
      p <- DimPlot(obj, group.by = "Parse_general_group2", label = T) + 
      theme(legend.position = "bottom") + ggtitle(i)
      LabelClusters(p, id = "Parse_general_group2", fontface = "bold", size = 5)
      print(p)
}

#SEE GENERAL GROUP IN DATAFRAME-START
#------------------------------------------------------------------------------------------------
#------------------------------------------------------------------------------------------------
#------------------------------------------------------------------------------------------------
df1 <- as.data.frame(table(Vpc1$Parse_general_group2))
df2 <-  as.data.frame(table(Vpc2$Parse_general_group2))
df3 <- as.data.frame(table(Vpc3$Parse_general_group2))
df4 <- as.data.frame(table(Vpc4$Parse_general_group2))

rownames(df1) <- df1$Var1
rownames(df2) <- df2$Var1
rownames(df3) <- df3$Var1
rownames(df4) <- df4$Var1

df$Var1 <- NULL
df1$Var1 <- NULL
df2$Var1 <- NULL
df3$Var1 <- NULL
df4$Var1 <- NULL

colnames(df1)[1] <- "WT Normoxia"
colnames(df2)[1] <- "WT Hypoxia"
colnames(df3)[1] <- "SPHK1 Normoxia"
colnames(df4)[1] <- "SPHK1 Hypoxia"

df <- cbind(df1, df2, df3, df4)


library(ggplot2)
library(tidyr)

df$Cell_Type <- rownames(df)

# Convert data frame to long format
df_long <- pivot_longer(df, cols = c("WT Normoxia", "WT Hypoxia", "SPHK1 Normoxia", "SPHK1 Hypoxia"),
                        names_to = "Condition", values_to = "Count")


library(gridExtra)
library(ggplot2) 
# Open a PNG device to save the output as a high-resolution image (300 dpi)
png("General_cell_types_sphk1_percentage.png", width = 5, height = 6, units = "in", res = 300) #7

# Arrange and save all plots in a grid with 3 columns
p

# Close the graphics device
dev.off()



# Create grouped bar plot
p <- ggplot(df_long, aes(x = Cell_Type, y = Count, fill = Condition)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = Count), 
          position = position_stack(vjust = 0.5), # Position the text labels in the middle of each bar section
          size = 3, color = "black") +
  labs(x = "Cell Type", y = "Count", title = "Comparison of Counts by Condition for Each Cell Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_brewer(palette = "Set1")



df_long$total <- NA
df_long$total[df_long$Condition == "WT Normoxia"] <- 9231
df_long$total[df_long$Condition == "WT Hypoxia"] <- 8609
df_long$total[df_long$Condition == "SPHK1 Normoxia"] <- 7442
df_long$total[df_long$Condition == "SPHK1 Hypoxia"] <- 7695


df_long$count_percent <- NA
df_long$count_percent <- (df_long$Count * 100) / df_long$total





p <- ggplot(df_long, aes(x = Cell_Type, y = count_percent, fill = Condition)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = sprintf("%.1f", count_percent)), 
          position = position_stack(vjust = 0.5), # Position the text labels in the middle of each bar section
          size = 3, color = "black") +
  labs(x = "Cell Type", y = "Count", title = "Comparison of Counts by Condition for Each Cell Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_brewer(palette = "Set1")


#SEE GENERAL GROUP IN DATAFRAME-END
#------------------------------------------------------------------------------------------------
#------------------------------------------------------------------------------------------------
#------------------------------------------------------------------------------------------------

columns <- c("Parse_general_group2", "general_group_w_na", "general_group_nounk")

for (i in columns){

SCT_SPHK1[[i]] <- NA
}



columns <- c("Parse_general_group2", "general_group_w_na", "general_group_nounk")
for (j in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
  obj <- get(j)
  yes <- colnames(obj)
  for(i in columns){
    RNA_SPHK1@meta.data[yes, i] <- obj@meta.data[yes, i]
  }
  }


columns <- c("Parse_general_group2", "general_group_w_na", "general_group_nounk")
for (j in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
  obj <- get(j)
  yes <- colnames(obj)
  for(i in columns){
    SCT_SPHK1@meta.data[yes, i] <- obj@meta.data[yes, i]
  }
  }


columns <- c("Parse_general_group2", "general_group_w_na", "general_group_nounk")

for(i in columns){
  p <- DimPlot(SCT_SPHK1, group.by = i, label = F) + 
  theme(legend.position = "bottom") + ggtitle(i)
  p <- LabelClusters(p, id = i, fontface = "bold", size = 5)
  print(p)
}


columns <- c("Parse_general_group2", "general_group_w_na", "general_group_nounk")


for(i in columns){
  filename <- paste0("SCT_", i, ".png")
  png(filename, width = 11, height = 11, units = "in", res = 300)
  p <- DimPlot(SCT_SPHK1, group.by = i, label = F) + 
  theme(legend.position = "bottom") + ggtitle(i)
  p <- LabelClusters(p, id = i, fontface = "bold", size = 3)
  dev.off()
  print(p)

  }

for(i in columns){
  filename <- paste0("RNA_", i, ".png")
  png(filename, width = 11, height = 11, units = "in", res = 300)
  p <- DimPlot(RNA_SPHK1, group.by = i, label = F) + 
  theme(legend.position = "bottom") + ggtitle(i)
  p <- LabelClusters(p, id = i, fontface = "bold", size = 3)
  print(p)
  dev.off()
   }

for(i in columns){
  p <- DimPlot(RNA_SPHK1, group.by = i, label = F) + 
  theme(legend.position = "bottom") + ggtitle(i)
  p <- LabelClusters(p, id = i, fontface = "bold", size = 5)
  print(p)
     }


RNA_SPHK1_list <- list(Vpc1 = Vpc1, Vpc2 = Vpc2, Vpc3 = Vpc3, Vpc4 = Vpc4)
rm(RNA_SPHK1_list)




```


```{r, fig.height=19, fig.width=25}



p <- DimPlot(RNA_SPHK1, group.by = "Parse_Ann", label = F) + 
  theme(legend.position = "bottom") + ggtitle("Parse_Ann")
LabelClusters(p, id = "Parse_Ann", fontface = "bold", size = 5)

yes <- colnames(Vpc1)
RNA_SPHK1$Parse_Ann <- NA
RNA_SPHK1$Parse_Ann[yes] <- Vpc1$Parse_Ann[yes]


colnames(Vpc1) <- paste0(colnames(Vpc1), "_1")
yes <- colnames(Vpc1)
RNA_SPHK1$Parse_Ann[yes] <- Vpc1$Parse_Ann_i[yes]

colnames(Vpc2) <- paste0(colnames(Vpc2), "_2")
yes <- colnames(Vpc2)
RNA_SPHK1$Parse_Ann[yes] <- Vpc2$Parse_Ann_i[yes]

colnames(Vpc3) <- paste0(colnames(Vpc3), "_3")
yes <- colnames(Vpc3)
RNA_SPHK1$Parse_Ann[yes] <- Vpc3$Parse_Ann_i[yes]


colnames(Vpc4) <- paste0(colnames(Vpc4), "_4")
yes <- colnames(Vpc4)
RNA_SPHK1$Parse_Ann[yes] <- Vpc4$Parse_Ann_i[yes]


p <- DimPlot(RNA_SPHK1, group.by = "Parse_Ann", label = F) + 
  theme(legend.position = "bottom") + ggtitle("Parse_Ann")
LabelClusters(p, id = "Parse_Ann", fontface = "bold", size = 5)

getwd()





library(gridExtra)
library(ggplot2) 
# Open a PNG device to save the output as a high-resolution image (300 dpi)
png("Parsal_Anno_tras_EC.png", width = 25, height = 19, units = "in", res = 300)

# Arrange and save all plots in a grid with 3 columns
DimPlot(Parsall_comb, label = T )

# Close the graphics device
dev.off()

getwd()

DimPlot(SCT_SPHK1, cells.highlight = colnames(SCT_SPHK1)[SCT_SPHK1$Parse_Ann %in% "Alveolar fibroblasts"])

FeaturePlot(SCT_SPHK1, "Fabp4", order = T)



Parsall_comb$Annotation_transfer_EC[Parsall_comb$Annotation_transfer_EC %in% "AT1"] <- "Mesothelial cells"
DimPlot(Parsall_comb, label = T )


Idents(Parsall_comb) <- Parsall_comb$Annotation_transfer_EC

DimPlot(Parsall_comb, label = T, group.by = "general_group2" )
DimPlot(Parsall_comb, label = T, group.by = "general_group" )


try <- subset(Parsall_comb, umap_2 > 6 & umap_1 < 10 & umap_1 > 0)


DimPlot(try)
table(try$general_group2)

yes <- colnames(try)[try$general_group2 %in% c("Endothelial cells", "Epithelial cells")]   #Lymphoid derived cells

DimPlot(Parsall_comb, cells.highlight = yes, raster = F)

Parsall_comb$general_group2[yes] <- "Lymphoid derived cells"

Parsall_comb$general_group_nounk <- Parsall_comb$general_group2


take <- colnames(uni_odd_seurat)

Parsall_comb$na_type <- NA
Parsall_comb$na_type[take] <- uni_odd_seurat$na_type[take]
getwd()

DimPlot(Parsall_comb, group.by = "na_type")

Parsall_comb$general_group_nounk[take] <- NA

DimPlot(Parsall_comb, group.by = "general_group_nounk")

Parsall_comb$general_group_w_na<- Parsall_comb$general_group_nounk

Parsall_comb$general_group_w_na[take] <- Parsall_comb$na_type[take]
DimPlot(Parsall_comb, group.by = "general_group_w_na")

```



```{r}
# MAKING THE TABLE

table(SCT_SPHK1$group)
df <- as.data.frame(table(SCT_SPHK1$Parse_Ann))

df1 <- as.data.frame(table(SCT_SPHK1$Parse_Ann[SCT_SPHK1$group == "WT Normoxia"]))
df2 <- as.data.frame(table(SCT_SPHK1$Parse_Ann[SCT_SPHK1$group == "WT Hypoxia"]))
df3 <-as.data.frame(table(SCT_SPHK1$Parse_Ann[SCT_SPHK1$group == "SPHK1 Normoxia"]))
df4 <-as.data.frame(table(SCT_SPHK1$Parse_Ann[SCT_SPHK1$group == "SPHK1 Hypoxia"]))

rownames(df) <- df$Var1

rownames(df1) <- df1$Var1
rownames(df2) <- df2$Var1
rownames(df3) <- df3$Var1
rownames(df4) <- df4$Var1

df$Var1 <- NULL
df1$Var1 <- NULL
df2$Var1 <- NULL
df3$Var1 <- NULL
df4$Var1 <- NULL

colnames(df)[1] <- "All_groups"
colnames(df1)[1] <- "WT Normoxia"
colnames(df2)[1] <- "WT Hypoxia"
colnames(df3)[1] <- "SPHK1 Normoxia"
colnames(df4)[1] <- "SPHK1 Hypoxia"





# Match rownames of df to rownames of df1
matched_indices <- match(rownames(df), rownames(df1))
df$WT_Normoxia<- NA
df$WT_Normoxia<- 0
df$WT_Normoxia[!is.na(matched_indices)] <- df1[matched_indices[!is.na(matched_indices)], "WT Normoxia"]

matched_indices <- match(rownames(df), rownames(df2))
df$WT_Hypoxia<- NA
df$WT_Hypoxia<- 0
df$WT_Hypoxia[!is.na(matched_indices)] <- df2[matched_indices[!is.na(matched_indices)], "WT Hypoxia"]

matched_indices <- match(rownames(df), rownames(df3))
df$SPHK1_Normoxia<- NA
df$SPHK1_Normoxia<- 0
df$SPHK1_Normoxia[!is.na(matched_indices)] <- df3[matched_indices[!is.na(matched_indices)], "SPHK1 Normoxia"]

matched_indices <- match(rownames(df), rownames(df4))
df$SPHK1_Hypoxia<- NA
df$SPHK1_Hypoxia<- 0
df$SPHK1_Hypoxia[!is.na(matched_indices)] <- df4[matched_indices[!is.na(matched_indices)], "SPHK1 Hypoxia"]

df <- df[!rownames(df) %in% "AT1", ]

# ILLUSTRATING DF TABLE

# Load necessary libraries
library(ggplot2)
library(tidyr)

df$Cell_Type <- rownames(df)

# Convert data frame to long format
df_long <- pivot_longer(df, cols = c("WT_Normoxia", "WT_Hypoxia", "SPHK1_Normoxia", "SPHK1_Hypoxia"),
                        names_to = "Condition", values_to = "Count")


library(gridExtra)
library(ggplot2) 
# Open a PNG device to save the output as a high-resolution image (300 dpi)
png("tagln_Smc_airway_vascular.png", width = 5, height = 9, units = "in", res = 300) #7

# Arrange and save all plots in a grid with 3 columns
DotPlot(Smc, features = "Tagln", group.by = "group", scale.min = 0)


# Close the graphics device
dev.off()



# Create grouped bar plot
p <- ggplot(df_long, aes(x = Cell_Type, y = Count, fill = Condition)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = Count), 
          position = position_stack(vjust = 0.5), # Position the text labels in the middle of each bar section
          size = 3, color = "black") +
  labs(x = "Cell Type", y = "Count", title = "Comparison of Counts by Condition for Each Cell Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_brewer(palette = "Set1")


```



```{r, fig.height=7, fig.width=19}
FeaturePlot(SCT_SPHK1, "Tagln", split.by = "group", order = T)
DotPlot(SCT_SPHK1, features = "Tagln", group.by = "group", #cols = c("blue", "red", "green", "orange")
        scale.min = 0)
DimPlot(SCT_SPHK1, label = T)

Smc <- subset(SCT_SPHK1, Parse_Ann %in% c("Vascular Smc", "Airway Smc"))
DotPlot(Smc, features = "Tagln", group.by = "group", scale.min = 0, split.by = "Parse_Ann")

Cl_21 <- subset(SCT_SPHK1, seurat_clusters %in% 21)
DotPlot(Cl_21, features = "Tagln", group.by = "group", scale.min = 0, split.by = "Parse_Ann", cols = c("blue", "red", "green", "orange", "pink"))

```

FeaturePlot(SCT_SPHK1, "Tagln", split.by = "group", order = T)

```{r}
RNA_SPHK1_list <- list(Vpc1 = Vpc1, Vpc2 = Vpc2, Vpc3 = Vpc3, Vpc4 = Vpc4)
```


```{r}
RNA_SPHK1$Parse_Ann_vcp1 <- RNA_SPHK1$Parse_Ann

```



#Transfer RNA_Sphk1 labels to SCT_Sphk1

```{r, fig.height=19, fig.width=19}
SCT_SPHK1$Parse_Ann <- NA
SCT_SPHK1$Parse_Ann <- RNA_SPHK1$Parse_Ann


p <- DimPlot(SCT_SPHK1, group.by = "Parse_Ann", label = F) + 
  theme(legend.position = "bottom") + ggtitle("Parse_Ann")
LabelClusters(p, id = "Parse_Ann", fontface = "bold", size = 5) 

```

```{r}


rm(list = ls())

Endo_RNA <- subset(RNA_SPHK1, Parse_general_group2 == "Endothelial cells")
Endo_SCT <- subset(SCT_SPHK1, Parse_general_group2 == "Endothelial cells")
Stroma_RNA <- subset(RNA_SPHK1, Parse_general_group2 == "Stromal cells")
Stroma_SCT <- subset(SCT_SPHK1, Parse_general_group2 == "Stromal cells")
for (i in c(Endo_RNA, Endo_SCT, Stroma_RNA, Stroma_SCT)){
  p <- DimPlot(i, group.by = "Parse_general_group2", label = T)
  print(p)
}


Endo_RNA <- subset(RNA_SPHK1, general_group_nounk == "Endothelial cells")
Endo_SCT <- subset(SCT_SPHK1, general_group_nounk == "Endothelial cells")
Stroma_RNA <- subset(RNA_SPHK1, general_group_nounk == "Stromal cells")
Stroma_SCT <- subset(SCT_SPHK1, general_group_nounk == "Stromal cells")
for (i in c(Endo_RNA, Endo_SCT, Stroma_RNA, Stroma_SCT)){
  p <- DimPlot(i, group.by = "general_group_nounk", label = T)
  print(p)
}

FeaturePlot(RNA_SPHK1, "Ptprc")
FeaturePlot(Endo_RNA, "Pecam1", order = T)
FeaturePlot(Endo_RNA, "Mki67", order = T)

DimPlot(RNA_SPHK1 )

#Clear Endothelial cell clusters

Endo_coord <- subset(RNA_SPHK1, umap_2 < -3)
Endo_coord <- subset(Endo_coord, umap_2 > -7.5 & umap_1 < 10, invert = T)

DimPlot(Endo_coord)

#Clear Stromal cell clusters

Stroma_coord <- subset(RNA_SPHK1, umap_1 < -3.5 & umap_1 > -11  & umap_2 > -10 & umap_2 < 10)
Stroma_coord <- subset(Stroma_coord, umap_2 > 3 & umap_1 > -5, invert = T)
Stroma_coord <- subset(Stroma_coord, umap_2 > -4 & umap_1 > -5, invert = T)
Stroma_coord <- subset(Stroma_coord, umap_1 < -4.3)

DimPlot(Stroma_coord)


#ENDO_SPHK1

Endo_coord <- ScaleData(Endo_coord, vars.to.regress = "percent.mt")
Endo_coord <- RunPCA(Endo_coord, npcs = 50)
Endo_coord <- RunUMAP(Endo_coord, dims = 1:30)
Endo_coord <- FindNeighbors(Endo_coord, dims = 1:30)
Endo_coord <- FindClusters(Endo_coord, resolution = 0.30)

DimPlot(Endo_SPHK1, group.by = "general_group_nounk", label = T)


table(Endo_SPHK1$orig.ident)


Vpc1 <- RNA_SPHK1_list[1]$Vpc1
Vpc2 <- RNA_SPHK1_list[2]$Vpc2
Vpc3 <- RNA_SPHK1_list[3]$Vpc3
Vpc4 <- RNA_SPHK1_list[4]$Vpc4

for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")) {
  obj <- get(i)
  obj <- subset(obj, cells = intersect(colnames(obj), colnames(Endo_coord)))
  assign(i, obj)
}



for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
    obj <- get(i)
    anchors <- FindTransferAnchors(
      reference = Nature_RNA_reference,         # Reference Seurat object (with known T cell labels)
  query = obj,                 # Query Seurat object (to which we want to transfer labels)
  normalization.method = "LogNormalize",       # Normalization method (use "SCT" if you did SCTransform or "SCT")
  reference.assay = "RNA",            # Assay in the reference Seurat object (usually "RNA" for raw or normalized counts)
  query.assay = "RNA",                # Assay in the query Seurat object
  dims = 1:30)
    #2- Second Tranfer labels
    Bis_TRANSITIVE_Elh <- TransferData(anchorset = anchors,
                             refdata = Nature_RNA_reference$annot,
                             dims = 1:30
                             )
    obj$annot_Nature <- Bis_TRANSITIVE_Elh$predicted.id
    assign(i, obj)
}


  Endo_coord$annot <- NA

for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
  obj <- get(i)
  yes <- colnames(obj)
  Endo_coord@meta.data[yes, "annot"] <- obj@meta.data[yes, "annot_Nature"]
  }
  
  DimPlot(Endo_coord, group.by = "annot1", label = T)
  Endo_coord$annot1 <- Endo_coord$annot
  
  Endo_coord$annot1[grepl("gCap", Endo_coord$annot)] <- "gCaps"
  
  DimPlot(Endo_coord, label = T)
  
  DefaultAssay(Endo_coord) <- "RNA"
  FeaturePlot(Endo_coord, "Gja5", order = T)

    DimPlot(Endo_coord, group.by = "annot1", label = T, split.by = "orig.ident") + NoLegend()
    
  Endo_coord$annot1[Endo_coord$annot1 %in% "Aerocytes"] <- "aCaps"
  Endo_coord$annot1[Endo_coord$annot1 %in% "Pulmonary vein"] <- "PVECs"
  Endo_coord$annot1[Endo_coord$annot1 %in% "Pulmonary artery"] <- "PAECs"
  Endo_coord$annot1[Endo_coord$annot1 %in% "Lymphatic EC"] <- "Lymphatic ECs"
  
  
  
  #Stroma_SPHK1
  
  Stroma_SPHK1 <- ScaleData(Stroma_coord, vars.to.regress = "percent.mt")
Stroma_SPHK1<- RunPCA(Stroma_SPHK1, npcs = 50)
Stroma_SPHK1 <- RunUMAP(Stroma_SPHK1, dims = 1:30)
Stroma_SPHK1 <- FindNeighbors(Stroma_SPHK1, dims = 1:30)
Stroma_SPHK1 <- FindClusters(Stroma_SPHK1, resolution = 0.30)

DimPlot(Stroma_SPHK1, group.by = "general_group_nounk", label = T)

Vpc1 <- RNA_SPHK1_list[1]$Vpc1
Vpc2 <- RNA_SPHK1_list[2]$Vpc2
Vpc3 <- RNA_SPHK1_list[3]$Vpc3
Vpc4 <- RNA_SPHK1_list[4]$Vpc4

for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")) {
  obj <- get(i)
  obj <- subset(obj, cells = intersect(colnames(obj), colnames(Stroma_SPHK1)))
  assign(i, obj)
}



for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
    obj <- get(i)
    anchors <- FindTransferAnchors(
      reference = Stromal_parse_again,         # Reference Seurat object (with known T cell labels)
  query = obj,                 # Query Seurat object (to which we want to transfer labels)
  normalization.method = "LogNormalize",       # Normalization method (use "SCT" if you did SCTransform or "SCT")
  reference.assay = "RNA",            # Assay in the reference Seurat object (usually "RNA" for raw or normalized counts)
  query.assay = "RNA",                # Assay in the query Seurat object
  dims = 1:30)
    #2- Second Tranfer labels
    Bis_TRANSITIVE_Elh <- TransferData(anchorset = anchors,
                             refdata = Stromal_parse_again$detailed_functional3,
                             dims = 1:30
                             )
    obj$Parse_StromAnn <- Bis_TRANSITIVE_Elh$predicted.id
    assign(i, obj)
}


for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
  obj <- get(i)
  yes <- colnames(obj)
  Stroma_SPHK1@meta.data[yes, "Parse_StromAnn"] <- obj@meta.data[yes, "Parse_StromAnn"]
}


  DimPlot(Stroma_SPHK1, group.by = "Parse_StromAnn", label = T, repel = T)
  DimPlot(Stroma_SPHK1, group.by = "general_group_nounk", label = T, repel = T)

  
  DefaultAssay(Stroma_SPHK1) <- "RNA"
  FeaturePlot(Stroma_SPHK1, "Acta2")

  FeaturePlot(Stroma_SPHK1, "Smtn")

DimPlot(Stromal_parse_again, label = T, group.by = "detailed_functional3", repel = T)
DimPlot(Stromal_parse_again, label = T, group.by = "AnnW_Ptprc")

Stromal_parse_again$detailed_functional3[Stromal_parse_again$AnnW_Ptprc %in% "Ptprc_pos_cells"] <- NA
  

rm(list = setdiff(ls(), c("Stroma_SPHK1", "Endo_SPHK1")))

DimPlot(Stroma_SPHK1, cells.highlight = colnames(Stroma_SPHK1)[Stroma_SPHK1$Parse_StromAnn %in% "Transitional Pericytes"])
#Myofibroblasts

for (i in c("Chrm2", "Itgbl1", "Acta2", "Aspn", "Lmod1", "F2r", "Wif1")){
    p <- FeaturePlot(Stroma_SPHK1, i, order = F, raster = F)
    print(p)
    }


pericyte_markers <- c("Kcnj8", "Vtn", "Abcc9", "Postn", "Pdgfrb", "Rgs5", "Acta2", "Notch3")
for (i in pericyte_markers){
    p <- FeaturePlot(Stroma_SPHK1, i, order = F, raster = F)
    print(p)
}


```

```{r, fig.height=11, fig.width=11}
library(celldex)
celldex::MouseRNAseqData()

mouse_ref <- MouseRNAseqData()

mouse_ref

library(SingleR)

test_assay <- GetAssayData(RNA_SPHK1)
predictions <- SingleR(test = test_assay, ref = mouse_ref, labels = mouse_ref$label.main)
RNA_SPHK1$celldex_labels <- predictions$labels 
DimPlot(RNA_SPHK1, group.by = "celldex_labels", label = TRUE, repel = T) #+ NoLegend()

```

```{r, fig.height=19, fig.width=11}
library(Azimuth)
library(Seurat)
#library(SeuratDisk)
library(SeuratData)

available_data <- AvailableData()
available_data[grep("Azimuth", available_data[, 3]), 1:3]
RNA_SPHK1 <- JoinLayers(RNA_SPHK1, assay.name = "RNA")

dene <- RunAzimuth(RNA_SPHK1, reference = "lungref", assay = "RNA")

DefaultAssay(RNA_SPHK1) <- "RNA"

DimPlot(dene, group.by = "predicted.ann_finest_level", label = TRUE, label.size = 3) + NoLegend()

RNA_SPHK1$Azimuth_labels <- dene$predicted.ann_finest_level
DimPlot(RNA_SPHK1, group.by = "Azimuth_labels", label = T) + NoLegend()

yes <- colnames(Stroma_SPHK1)
Stroma_SPHK1$Azimuth_labels <- NA
Stroma_SPHK1$Azimuth_labels[yes] <- RNA_SPHK1$Azimuth_labels[yes]

DimPlot(Stroma_SPHK1, group.by = "Azimuth_labels", label = T) #+ NoLegend()
DimPlot(Stroma_SPHK1, group.by = "Parse_StromAnn2", label = T) + NoLegend()


```
```{r}
DimPlot(Stroma_SPHK1, cells.highlight = colnames(Stroma_SPHK1)[Stroma_SPHK1$Azimuth_labels %in% "Peribronchial fibroblasts"]) + ggtitle("Pericytes")
DimPlot(Stroma_SPHK1, cells.highlight = colnames(Stroma_SPHK1)[Stroma_SPHK1$Parse_Ann %in% "Vascular Smc"]) 

```

#Smc_pericytes

```{r, fig.height=8, fig.width=15}

DimPlot(Stroma_SPHK1)
Stroma_SPHK1$Parse_StromAnn2 <- Stroma_SPHK1$Parse_StromAnn
Stroma_SPHK1$Parse_StromAnn2[Stroma_SPHK1$Parse_StromAnn %in% c("Airway Smc", "Vascular Smc")] <- "Smooth muscle"

Perismc <- subset(Stroma_SPHK1, umap_1 < -6)
Perismc2 <- subset(Perismc, Parse_StromAnn2 %in% c("Smooth muscle", "Transitional Pericytes", "Pericytes"))

DimPlot(sphk1_perismc, group.by = "Parse_StromAnn2", split.by = "group", pt.size = 2)
FeaturePlot(Perismc, "Acta2")

DimPlot(Perismc, label = T)


Perismc <- JoinLayers(Perismc, assay = "RNA")
Marker <- FindMarkers(Perismc, ident.1 = 4, only.pos = T, min.pct = 0.25)

Marker <- Marker %>% 
  top_n(n=33, wt = avg_log2FC)






Degs_in_real_pos <- FindMarkers(fibroblast, ident.1 = "real_pos", ident.2 = "deneme")
Idents(fibroblast) <- fibroblast$seurat_clusters

Degs_in_real_pos <- Degs_in_real_pos %>% 
  filter(p_val < 0.5 & avg_log2FC >= 0.6 ) %>%  #
  filter(pct.1 - pct.2 > 0.100)


Marker <- FindMarkers(Parsall_comb, ident.1 = 13, only.pos = T, min.pct = 0.25, logfc.threshold = 0.10)
Marker_13 <- Marker %>% 
   top_n(n =51, wt = avg_log2FC)


DimPlot(Perismc, group.by = "Azimuth_labels", split.by = "orig.ident", pt.size = 2)

DimPlot(Perismc, group.by = "Azimuth_labels", split.by = "orig.ident", pt.size = 2, cells.highlight = colnames(Perismc)[Perismc$Azimuth_labels %in% "SM activated stress response"], raster = F)

DimPlot(Perismc, cells.highlight = colnames(Perismc)[Perismc$Azimuth_labels %in% "SM activated stress response"])
table(Perismc$Azimuth_labels)

RNA_SPHK1$group1 <- ifelse(RNA_SPHK1$orig.ident %in% "Vpc4", "SPHK1 Hypoxia",
                          ifelse(RNA_SPHK1$orig.ident %in% "Vpc3", "SPHK1 Normoxia",
                                 ifelse(RNA_SPHK1$orig.ident %in% "Vpc2", "WT Hypoxia", "WT Normoxia")))

unique(factor(RNA_SPHK1$group))
FeaturePlot(RNA_SPHK1, "Pecam1", split.by = "group")

RNA_SPHK1$group <- factor(RNA_SPHK1$group, levels = c("WT_Normoxia", "WT_Hypoxia", "SPHK1_Normoxia", "SPHK1_Hypoxia"))





?FeaturePlot



table(RNA_SPHK1$group)

yes <- colnames(sphk1_perismc)

sphk1_perismc$group <- NA
sphk1_perismc$group[yes] <- RNA_SPHK1$group[yes]

RNA_SPHK1$orig.ident

sphk1_perismc$group <- factor(sphk1_perismc$group, levels = c("WT_Normoxia", "WT_Hypoxia", "SPHK1_Normoxia", "SPHK1_Hypoxia"))

 ident_pairs <- list(
    c("WT_Hypoxia", "WT_Normoxia"),
    c("SPHK1_Hypoxia", "WT_Hypoxia"),
    c("SPHK1_Normoxia", "WT_Normoxia"),
    c("SPHK1_Hypoxia", "SPHK1_Normoxia")
 
 
 
 table(sphk1_perismc$group[sphk1_perismc$Parse_StromAnn2 %in% "Smooth muscle"])
 smc <- subset(sphk1_perismc, Parse_StromAnn2 %in% "Smooth muscle")
 
 Idents(sphk1_perismc) <- sphk1_perismc$group
 table(smc$group)
 
Marker <- FindMarkers(sphk1_perismc, ident.1 = "SPHK1_Hypoxia", ident.2 = "WT_Normoxia", only.pos = T, group.by = "group")
Marker <- Marker %>% 
  filter(p_val_adj < 0.05) 

%>% 
top_n(n =33, wt = avg_log2FC)


  


table(sphk1_perismc$group)

write.csv(Marker, "SMC_WT_Normoxia_vs_WT_Hypoxia_2.csv")




table(sphk1_perismc$group[sphk1_perismc$Parse_StromAnn2 %in% "Smooth muscle"])

table(sphk1_perismc$Parse_StromAnn2)

#----------------------------------------------------------------------------------------
#----------------------------------------------------------------------------------------
#----------------------------------------------------------------------------------------
#REGRESSING RIBOSOMAL GENES
ribosomal_genes <- grep("^Rpl|^Rps", rownames(smc), value = TRUE)
smc <- PercentageFeatureSet(smc, features = ribosomal_genes, col.name = "percent.ribo")

smc <- ScaleData(
  object = smc,
  vars.to.regress = "percent.ribo"
)

smc <- FindVariableFeatures(smc, selection.method = "vst", nfeatures = 2000)

DefaultAssay(smc) <- "RNA"
smc <- RunPCA(smc, npcs = 50)
smc <- RunUMAP(smc, dims = 1:30)
smc <- FindNeighbors(smc, dims = 1:30)
smc <- FindClusters(smc, resolution = 0.30)

DimPlot(smc)
#----------------------------------------------------------------------------------------
#----------------------------------------------------------------------------------------
#----------------------------------------------------------------------------------------

FeaturePlot(sphk1_perismc, "Acta2")

DimPlot(sphk1_perismc, label = T)
```

```{r}

#Idents(Endo_SPHK1) <- Endo_SPHK1$group
#Endo_SPHK1 <- JoinLayers(Endo_SPHK1, assay = "RNA")
find_and_save_markers <- function(seurat_obj) {
  # Define the identifier pairs within the function
  for (i in sub_endo) {
    seurat_obj <- subset(Endo_SPHK1, annot1 %in% i)
      ident_pairs <- list(
    c("WT_Hypoxia", "WT_Normoxia"),
    c("SPHK1_Hypoxia", "WT_Hypoxia"),
    c("SPHK1_Normoxia", "WT_Normoxia"),
    c("SPHK1_Hypoxia", "SPHK1_Normoxia")
      )
        # Loop through each pair and find markers
        for (pair in ident_pairs) {
              # Extract ident.1 and ident.2 from the pair
              ident_1 <- pair[1]
                  ident_2 <- pair[2]
                      # Find markers
                      markers <- FindMarkers(seurat_obj, ident.1 = ident_1, ident.2 = ident_2, only.pos = FALSE)
                      
                          # Select top 33 markers based on avg_log2FC
                          top_markers <- markers %>% 
                                  filter(p_val_adj < 0.05) %>% 
                                  slice_max(order_by = avg_log2FC, n = 50)
                          
                              # Create a filename based on the identifiers
                              filename <- paste0(i, "_", ident_1, "_vs_", ident_2, ".csv")
                                  # Write the markers to a CSV file
                                  write.csv(top_markers, filename)
                                      # Print a message indicating progress
                                      print(paste("Markers for", ident_1, "vs", ident_2, "saved to", filename))
        }
  }
}

# Run the function
find_and_save_markers(Endo_SPHK1)



```



```{r}

Idents(smc) <- smc$group
#Endo_SPHK1 <- JoinLayers(Endo_SPHK1, assay = "RNA")
find_and_save_markers <- function(seurat_obj) {
  # Define the identifier pairs within the function
      ident_pairs <- list(
    c("WT_Hypoxia", "WT_Normoxia"),
    c("SPHK1_Hypoxia", "WT_Hypoxia"),
    c("SPHK1_Normoxia", "WT_Normoxia"),
    c("SPHK1_Hypoxia", "SPHK1_Normoxia")
      )
        # Loop through each pair and find markers
        for (pair in ident_pairs) {
              # Extract ident.1 and ident.2 from the pair
              ident_1 <- pair[1]
                  ident_2 <- pair[2]
                      # Find markers
                      markers <- FindMarkers(seurat_obj, ident.1 = ident_1, ident.2 = ident_2, only.pos = FALSE)
                      
                          # Select top 33 markers based on avg_log2FC
                          top_markers <- markers %>% 
                                  filter(p_val_adj < 0.05) %>% 
                                  #filter(p_val_adj < 0.05) %>% 
                                  #slice_max(order_by = avg_log2FC, n = 50)
                                  slice_max(order_by = p_val_adj, n = 20)
                          
                              # Create a filename based on the identifiers
                              filename <- paste0("SMC_ns_", "_", ident_1, "_vs_", ident_2, ".csv")
                                  # Write the markers to a CSV file
                                  write.csv(top_markers, filename)
                                      # Print a message indicating progress
                                      print(paste("Markers for", ident_1, "vs", ident_2, "saved to", filename))
        }
  }


# Run the function
find_and_save_markers(smc)

```



```{r, fig.height=6, fig.width=19}
library(clusterProfiler)
library(org.Hs.eg.db)  # For human, use org.Mm.eg.db for mouse
library(enrichplot)
library(ggplot2)

DimPlot(Endo_SPHK1, group.by = "annot1", label = T, split.by = "group")

#Constructing the group name with ifelse
Endo_SPHK1$group <- ifelse(grepl("_1$", colnames(Endo_SPHK1)), "WT Normoxia",
                               ifelse(grepl("_2$", colnames(Endo_SPHK1)), "WT Hypoxia",
                                      ifelse(grepl("_3$", colnames(Endo_SPHK1)), "SPHK1 Normoxia", "SPHK1 Hypoxia")))
```
```{r, fig.height=19, fig.width=19}


p <- DimPlot(RNA_SPHK1, label = F, group.by = "Parse_Ann") + NoLegend()
    LabelClusters(p, id = "Parse_Ann", fontface = "bold", size = 5)
    
    table(smc$group)

```


```{r, fig.height=7, fig.width=8}

FeaturePlot(RNA_SPHK1, "Sphk1", order = F)
FeaturePlot(sphk1_perismc, "Sphk1", order = T, split.by = "group")
FeaturePlot(Stromal_parse_again, "Sphk1", order = T)
DimPlot(Stromal_parse_again, raster = F, group.by = "detailed_functional3", label = T)

DotPlot(RNA_SPHK1, "Sphk1", group.by = "group", split.by = "Parse_general_group2", cols = c("red", "blue", "green", "orange", "yellow"))

AT1 <- subset(RNA_SPHK1, Parse_Ann %in% "AT1 cells")
DimPlot(sphk1_perismc)


DotPlot(AT1, "Sphk1", group.by = "group")

DotPlot(sphk1_perismc, "Sphk1", group.by = "group")


smc_tr <- subset(sphk1_perismc, Parse_StromAnn2 %in% c("Smooth muscle", "Transitional Pericytes"))


DotPlot(sphk1_perismc, "Sphk2", group.by = "group")

peri <- subset(sphk1_perismc, Parse_StromAnn2 %in% c("Pericytes"))

table(sphk1_perismc$Parse_StromAnn2)



DotPlot(Endo_SPHK1, "Sphk2", group.by = "group")


rownames(RNA_SPHK1)[grep("Sk", rownames(RNA_SPHK1))]


for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
  obj <- get(i)
  p <- DotPlot(obj, "Sphk1")
  print(p)
}

DimPlot(Vpc1, label = T)


for (i in list("Vpc1", "Vpc2", "Vpc3", "Vpc4")){
  obj <- get(i)
  p1 <- DimPlot(Vpc1, label = T)
  p2 <- DimPlot(Vpc1, label = T, group.by = "Parse_Ann_i") + NoLegend()
  print(p1)
  print(p2)
}



DimPlot(Vpc1, label = T, group.by = "Parse_Ann_i") + NoLegend()

rm(list = ls())

DefaultAssay(Integ_SCT_mouse) <- "SCT"
FeaturePlot(Integ_SCT_mouse, "Sphk1")

DimPlot(Integ_SCT_mouse, group.by = "IntegAnn", label = T) + NoLegend()


getwd()

```


#11/20/2024 DUTIES

```{r}

genes <- c("Sphk1", "Sphk2", "Spp1", "Spp2", "Cers1", "Cers2", "Cers3", "Cers4", "Cers5", "Cers6", "Degs1", "Ugcg","Sptlc1", "Sgpl1", "S1pr1", "S1pr2", "S1pr3", "S1pr4", "S1pr5", "Igsf3", "Smpd1", "Galc", "Gba", "Smpd2", "Smpd3",  "Asah1", "Asah2",  "Acer1", "Acer2", "Acer3",  "Sgms1", "Sgms2","Ifng", "Cxcl10", "Col4a3bp", "Lpp")
#Whole lung
  #featureplot
for (i in genes){
  f <- paste0("featureplots/Whole_lung_", i, ".png")
  png(f, width = 19, height = 5, units = "in", res = 300)
  p <- FeaturePlot(RNA_SPHK1, features = i, split.by = "group")
  print(p)
  dev.off()
}
  
  #dotplot
for (i in genes){
  f <- paste0("dotplots/Whole_lung_", i, ".png")
  png(f, width = 7, height = 5, units = "in", res = 300)
  p <- DotPlot(RNA_SPHK1, features = i, group.by = "group1")
  print(p)
  dev.off()
}


#Smooth muscle-pericytes
  #featureplot
for (i in genes){
  f <- paste0("featureplots/Smc_pericyte_", i, ".png")
  png(f, width = 15, height = 5, units = "in", res = 300)
  p <- FeaturePlot(sphk1_perismc, features = i, split.by = "group")
  print(p)
  dev.off()
}
  
  #dotplot
for (i in genes){
  f <- paste0("dotplots/Smc_pericyte_", i, ".png")
  png(f, width = 7, height = 5, units = "in", res = 300)
  p <- DotPlot(sphk1_perismc, features = i, group.by = "group1")
  print(p)
  dev.off()
}



#Only Smooth muscle-
  #featureplot
for (i in genes){
  f <- paste0("featureplots/Only_Smc_", i, ".png")
  png(f, width = 15, height = 5, units = "in", res = 300)
  p <- FeaturePlot(smc, features = i, split.by = "group")
  print(p)
  dev.off()
}
  
  #dotplot
for (i in genes){
  f <- paste0("dotplots/Only_Smc_", i, ".png")
  png(f, width = 7, height = 5, units = "in", res = 300)
  p <- DotPlot(smc, features = i, group.by = "group1")
  print(p)
  dev.off()
}
  

#Smc_w_transitional
  #featureplot
for (i in genes){
  f <- paste0("featureplots/Smc_w_transitional_", i, ".png")
  png(f, width = 15, height = 5, units = "in", res = 300)
  p <- FeaturePlot(smc, features = i, split.by = "group")
  print(p)
  dev.off()
}
  
  #dotplot
for (i in genes){
  f <- paste0("dotplots/Smc_w_transitional_", i, ".png")
  png(f, width = 7, height = 5, units = "in", res = 300)
  p <- DotPlot(smc, features = i, group.by = "group1")
  print(p)
  dev.off()
}
  

#Endothelial cells


for (i in genes){
  f <- paste0("featureplots/Endothelial_subset_featureplots", i, ".png")
  png(f, width = 19, height = 5, units = "in", res = 300)
  p <- tryCatch(
      {
        FeaturePlot(Endo_SPHK1, features = i, split.by = "group")
      },
      error = function(e) {
        # Handle error and print message
        print(paste("Error while creating FeaturePlot for gene:", i))
        print(e)
        dev.off()
        NULL
      }
    )
    # Print and save the plot if successful
  if (!is.null(p)) {
      print(p)
  } else {
      next
    }
  dev.off()
  }



sub_endo <- unique(Endo_SPHK1$annot1)
  
  #dotplot WORKED
sub_endo <- unique(Endo_SPHK1$annot1)
for (i in genes){
  for(j in sub_endo){
  f <- paste0("dotplots/Endothelial_subset_dotplots/", j, "_", i, ".png")
  sub_seurat <- subset(Endo_SPHK1, annot1 %in% j)
  png(f, width = 7, height = 5, units = "in", res = 300)
  p <- DotPlot(sub_seurat, features = i, group.by = "group1")
  print(p)
  dev.off()
  }
}




# THSI WORKED WE SUBSET ALL CELLS IN FEATURE PLOT



sub_endo <- unique(Endo_SPHK1$annot1)

# Loop through each gene and subgroup
for (i in genes) {
  for (j in sub_endo) {
    # Construct the file path for saving the plot
    f <- paste0("featureplots/Endothelial_subset_featureplots/", j, "_", i, ".png")
    
    # Subset the Seurat object by subgroup
    sub_seurat <- subset(Endo_SPHK1, annot1 %in% j)

    # Check if subset is empty before proceeding
    if (ncol(sub_seurat) == 0) {
      print(paste("Skipping empty subset for group:", j))
      next  # Skip to the next iteration if the subset is empty
    }

    # Check for missing values in the feature data
    if (any(is.na(FetchData(sub_seurat, vars = i)))) {
      print(paste("Skipping gene:", i, "in group:", j, "due to missing values."))
      next  # Skip to the next iteration if there are missing values in the data
    }

    # Open PNG device to save the plot
    png(f, width = 19, height = 5, units = "in", res = 300)

    # Create the FeaturePlot for the specific gene in the subset
    p <- tryCatch(
      {
        FeaturePlot(sub_seurat, features = i, split.by = "group")
      },
      error = function(e) {
        # Handle error and print message
        print(paste("Error while creating FeaturePlot for gene:", i, "in group:", j))
        print(e)
        NULL
      }
    )

    # Print and save the plot if successful
    if (!is.null(p)) {
      print(p)
    }

    # Close the PNG device
    dev.off()
  }
}
























 
 
 getwd() 
  
png("dene.png", width = 7, height = 5, units = "in", res = 300)
 DotPlot(RNA_SPHK1, features = "Pecam1", group.by = "group")
dev.off()

 
unique(factor(RNA_SPHK1$group))




#Constructing the group name with ifelse
Endo_SPHK1$group <- ifelse(grepl("_1$", colnames(Endo_SPHK1)), "WT_Normoxia",
                               ifelse(grepl("_2$", colnames(Endo_SPHK1)), "WT_Hypoxia",
                                      ifelse(grepl("_3$", colnames(Endo_SPHK1)), "SPHK1_Normoxia", "SPHK1_Hypoxia")))

Endo_SPHK1$group1 <- Endo_SPHK1$group
Endo_SPHK1$group <- factor(Endo_SPHK1$group, levels = c("WT_Normoxia", "WT_Hypoxia", "SPHK1_Normoxia", "SPHK1_Hypoxia"))
Endo_SPHK1$group1 <- factor(Endo_SPHK1$group1, levels = rev(c("WT_Normoxia", "WT_Hypoxia", "SPHK1_Normoxia", "SPHK1_Hypoxia")))
  
?factor


  
#IFNA1 =Ifnar1
#"Col4a3bp" = Cert

rownames(RNA_SPHK1)[grep("Ifn", rownames(RNA_SPHK1))]

FeaturePlot(Endo_SPHK1, "Fabp4")

DimPlot(Endo_SPHK1, group.by = "annot1")

```

#PATHWAY ANALYSIS- ELHAMDULILLAH!!!!!!!!!!!!!!!!!!!!!!!!!!

```{r}

library(org.Mm.eg.db)

RNA_SPHK1 <-  readRDS("C:/Users/skacar/OneDrive - Indiana University/PULMONARY POST DOC/___SPHK1_PROJECT____/Rna_Sphk1_11_15_24.Rds") #Integration after RNA LogNormalize of SPHK1 (4 samples)Vcp1, WT, Vcp2, WT-Hypoxia, Vcp3, Sphk1-WT, Vcp4, Sphk1-Hypoxia

WT_Normoxia <- subset(RNA_SPHK1, group %in% "WT_Normoxia")
WT_Hypoxia  <- subset(RNA_SPHK1, group %in% "WT_Hypoxia")
exp_norm <- as.matrix(WT_Normoxia@assays[["RNA"]]@layers[["data"]])
exp_hyp <- as.matrix(WT_Hypoxia@assays[["RNA"]]@layers[["data"]])


ref <- rowMeans(exp_norm)
sample <- rowMeans(exp_hyp)
rownames <- rownames(RNA_SPHK1)
names(ref) <- rownames
names(sample) <- rownames

comb <- cbind(ref, sample)
comb <- as.data.frame(comb)
comb$Entrezid <- NA

# Convert gene symbols to Entrez IDs
gene_symbols <- rownames(comb)  # Assuming these are your gene symbols
entrez_ids <- mapIds(org.Mm.eg.db, 
                     keys = gene_symbols, 
                     column = "ENTREZID", 
                     keytype = "SYMBOL", 
                     multiVals = "first")

comb$Entrezid <- entrez_ids

filtered_comb <- comb[!is.na(comb$Entrezid), ]
rownames(filtered_comb) <- filtered_comb$Entrezid

filtered_comb <- as.data.frame(filtered_comb)
filtered_comb <- as.matrix(filtered_comb[ , c("ref", "sample")])
rownames <- rownames(filtered_comb)
#change to numeric forcefully
filtered_comb <- apply(filtered_comb, 2, as.numeric)
rownames(filtered_comb) <- rownames
any(!sapply(filtered_comb, is.numeric))  # Should return FALSE

library(gageData)
data(kegg.sets.mm)

gage_results <- gage(exprs = filtered_comb, gsets = kegg.sets.mm)

# View results
print(gage_results$greater)  # Up-regulated pathways
print(gage_results$less)     #

View(gage_results$greater)

write.csv(gage_results$greater, "with_means_gage.csv")




```



#TRY TO USE EXPRESSION MATRIXES -NULL

```{r}
rm(list = ls())

library(org.Mm.eg.db)
library(gageData)

RNA_SPHK1 <-  readRDS("C:/Users/skacar/OneDrive - Indiana University/PULMONARY POST DOC/___SPHK1_PROJECT____/Rna_Sphk1_11_15_24.Rds") #Integration after RNA LogNormalize of SPHK1 (4 samples)Vcp1, WT, Vcp2, WT-Hypoxia, Vcp3, Sphk1-WT, Vcp4, Sphk1-Hypoxia

WT_Normoxia <- subset(RNA_SPHK1, group %in% "WT_Normoxia")
WT_Hypoxia  <- subset(RNA_SPHK1, group %in% "WT_Hypoxia")
exp_norm <- as.matrix(WT_Normoxia@assays[["RNA"]]@layers[["data"]])
exp_hyp <- as.matrix(WT_Hypoxia@assays[["RNA"]]@layers[["data"]])
#ADD COL AND ROW NAMES CELLS AND GENES I MEAN
colnames(exp_norm) <- colnames(WT_Normoxia)
colnames(exp_hyp) <- colnames(WT_Hypoxia)
rownames(exp_norm) <- rownames(WT_Normoxia)
rownames(exp_hyp) <- rownames(WT_Hypoxia)


# Convert gene symbols to Entrez IDs
gene_symbols <- rownames(exp_norm)  # Assuming these are your gene symbols
entrez_ids <- mapIds(org.Mm.eg.db, 
                     keys = gene_symbols, 
                     column = "ENTREZID", 
                     keytype = "SYMBOL", 
                     multiVals = "first")

# Identify rows with valid Entrez IDs
valid_rows <- !is.na(entrez_ids)
# Filter the matrices
exp_norm <- exp_norm[valid_rows, ]
exp_hyp <- exp_hyp[valid_rows, ]

entrez_ids <- entrez_ids[valid_rows]
rownames(exp_norm) <- entrez_ids
rownames(exp_hyp) <- entrez_ids

exprs <- cbind(exp_norm, exp_hyp)

# Define reference and sample columns
ref_cols <- 1:ncol(exp_norm)
samp_cols <- (ncol(exp_norm) + 1):ncol(exprs)



#CHOOSE AS PROFILES
# Aggregate by averaging across cells for each group
ref_profile <- rowMeans(exprs[, ref_cols])  # WT_Normoxia
samp_profile <- rowMeans(exprs[, samp_cols])  # WT_Hypoxia

# Create a pseudobulk matrix
exprs_pseudobulk <- cbind(ref_profile, samp_profile)

library(gageData)
data("kegg.mm.gs")
# Run GAGE on pseudobulk profiles
gage_results <- gage(exprs = exprs_pseudobulk, gsets = kegg.sets.mm, ref = 1, samp = 2, compare = "unpaired")




class(gage_results$greater
write.csv(gage_results$greater, "all_Cells_group_gage.csv")


```




#USE DEGS instead of NORMZALIZED MATRIX- ELHAMDULILLAH!!!!!

#WT_Hypoxia vs WT_Normoxia

```{r}
library(Seurat)
degs <- FindMarkers(RNA_SPHK1, ident.1 = "WT_Hypoxia", ident.2 = "WT_Normoxia", assay = "RNA", group.by = "group")
significant_degs <- degs[degs$p_val_adj < 0.05 & (degs$pct.1 > 0.1 | degs$pct.2 > 0.1),  ]

library(org.Mm.eg.db)
entrez_ids <- mapIds(org.Mm.eg.db,
                     keys = rownames(significant_degs),
                     column = "ENTREZID",
                     keytype = "SYMBOL",
                     multiVals = "first")
names(entrez_ids) <- rownames(significant_degs)

entrez_valid <- entrez_ids[!is.na(entrez_ids)]
significant_degs <- significant_degs[names(entrez_valid), ]


exprs_degs <- matrix(significant_degs$avg_log2FC, ncol = 1)
rownames(exprs_degs) <- entrez_valid


library(gageData)
data("kegg.sets.mm")
gage_results <- gage(exprs = exprs_degs, gsets = kegg.sets.mm, ref = NULL, samp = NULL, compare = "unpaired")

p <- gage_results$stats
#r <- gage_results$less
P <- as.data.frame(p)

P$mmu <- NA
P$mmu <- rownames(P)
# Remove the first word (everything before the first space) from rownames
P$mmu <- sub(" .*", "", P$mmu)
rownames(P) <- sub("^[^ ]+ ", "", rownames(P))
P$pathways <- NA
P$pathways <- rownames(P)


P <- P[order(-P$stat.mean), ]
#P <- P[-1, ] EXTRACT ROWS AS NEEDED
top_df <- head(P, 20)

```



```{r}
library(ggplot2)

p <- ggplot(top_df, aes(x = reorder(pathways, stat.mean), y = stat.mean)) +
    geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +
   labs(title = "WT_Normoxia vs WT_Hypoxia for Whole Lung", x = "Pathways", y = "Mean Enrichment Score (stat.mean)") +
  theme_minimal()

png("PATHWAYS/WT_Normoxia vs WT_Hypoxia for Whole Lung_no_ribosome.png", width = 7, height = 5, units = "in", res = 300)
p
dev.off


```




#The other pairs

```{r}

 ident_pairs <- list(
    c("WT_Hypoxia", "WT_Normoxia"),
    c("SPHK1_Hypoxia", "WT_Hypoxia"),
    c("SPHK1_Normoxia", "WT_Normoxia"),
    c("SPHK1_Hypoxia", "SPHK1_Normoxia")
    
```


#DO ALL PAIRWISE COMPARISONS GAGE KEGG
```{r}

ident_pairs <- list(
c("WT_Hypoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "WT_Hypoxia"),
c("SPHK1_Normoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "SPHK1_Normoxia"),
c("WT_Normoxia", "WT_Hypoxia"),
c("WT_Hypoxia", "SPHK1_Hypoxia"),
c("WT_Normoxia", "SPHK1_Normoxia"),
c("SPHK1_Normoxia", "SPHK1_Hypoxia")
)
        # Loop through each pair and find markers
for (pair in ident_pairs) {
  # Extract ident.1 and ident.2 from the pair
  ident_1 <- pair[1]
  ident_2 <- pair[2]
  library(Seurat)
  degs <- FindMarkers(sphk1_perismc, ident.1 = ident_2, ident.2 = ident_1, assay = "RNA", group.by = "group")
  significant_degs <- degs[degs$p_val_adj < 0.05 & (degs$pct.1 > 0.1 | degs$pct.2 > 0.1),  ]
  library(org.Mm.eg.db)
  entrez_ids <- mapIds(org.Mm.eg.db,
                     keys = rownames(significant_degs),
                     column = "ENTREZID",
                     keytype = "SYMBOL",
                     multiVals = "first")
  names(entrez_ids) <- rownames(significant_degs)
  entrez_valid <- entrez_ids[!is.na(entrez_ids)]
  significant_degs <- significant_degs[names(entrez_valid), ]
  exprs_degs <- matrix(significant_degs$avg_log2FC, ncol = 1)
  rownames(exprs_degs) <- entrez_valid
  
  library(gageData)
  data("kegg.sets.mm")
  gage_results <- gage(exprs = exprs_degs, gsets = kegg.sets.mm, ref = NULL, samp = NULL, compare = "unpaired")
  p <- gage_results$stats
  #r <- gage_results$less
  P <- as.data.frame(p)
  P$mmu <- NA
  P$mmu <- rownames(P)
  # Remove the first word (everything before the first space) from rownames
  P$mmu <- sub(" .*", "", P$mmu)
  rownames(P) <- sub("^[^ ]+ ", "", rownames(P))
  P$pathways <- NA
  P$pathways <- rownames(P)
  P <- P[order(-P$stat.mean), ]
  if ("Ribosome" %in% rownames(P[1:20, ])) {
  # Remove the row corresponding to "Ribosome"
  P <- P[rownames(P) != "Ribosome", ]
}
  top_df <- head(P, 20)
  library(ggplot2)
  plot <- ggplot(top_df, aes(x = reorder(pathways, stat.mean), y = stat.mean)) +
    geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +
   labs(title = paste0(ident_2, "_vs_", ident_1, " for Pericyte_Smc"), x = "Pathways", y = "Mean Enrichment Score (stat.mean)") +
  theme_minimal()
  png(paste0("./PATHWAYS/", ident_2, "_vs_", ident_1, " for Pericyte_Smc.png"), width= 7, height = 5, units = "in", res = 300)
  plot
  print(plot)
  dev.off()
}
```



```{r}

library(ggplot2)

p <- ggplot(top_df, aes(x = reorder(pathways, stat.mean), y = stat.mean)) +
    geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +
   labs(title = paste0(ident_2, "_vs_", ident_1, " for Whole Lung"), x = "Pathways", y = "Mean Enrichment Score (stat.mean)") +
  theme_minimal()

png(paste0("./PATHWAYS/", ident_2, "_vs_", ident_1, " for Whole Lung.png"), width = 7, height = 5, units = "in", res = 300)
p
dev.off()

```






#from gage results u can continue
```{r, fig.height=4, fig.width=10}


ident_pairs <- list(
c("WT_Hypoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "WT_Hypoxia"),
c("SPHK1_Normoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "SPHK1_Normoxia"),
c("WT_Normoxia", "WT_Hypoxia"),
c("WT_Hypoxia", "SPHK1_Hypoxia"),
c("WT_Normoxia", "SPHK1_Normoxia"),
c("SPHK1_Normoxia", "SPHK1_Hypoxia")
)
        # Loop through each pair and find markers
for (pair in ident_pairs) {
  # Extract ident.1 and ident.2 from the pair
  ident_1 <- pair[1]
  ident_2 <- pair[2]
  library(Seurat)
  degs <- FindMarkers(RNA_SPHK1, ident.1 = ident_2, ident.2 = ident_1, assay = "RNA", group.by = "group")
  significant_degs <- degs[degs$p_val_adj < 0.05 & (degs$pct.1 > 0.1 | degs$pct.2 > 0.1),  ]
  library(org.Mm.eg.db)
  entrez_ids <- mapIds(org.Mm.eg.db,
                     keys = rownames(significant_degs),
                     column = "ENTREZID",
                     keytype = "SYMBOL",
                     multiVals = "first")
  names(entrez_ids) <- rownames(significant_degs)
  entrez_valid <- entrez_ids[!is.na(entrez_ids)]
  significant_degs <- significant_degs[names(entrez_valid), ]
  exprs_degs <- matrix(significant_degs$avg_log2FC, ncol = 1)
  rownames(exprs_degs) <- entrez_valid
  
  library(ReactomePA)
  library(enrichplot)
  pathway_results <- enrichPathway(gene = rownames(exprs_degs), organism = "mouse", pvalueCutoff = 0.05)
  #ADDING LOG VALUES TO PATHWAY ANALYSIS
  pathway_results@result$logFC <- sapply(pathway_results@result$geneID, function(genes) {
  # Split geneID into individual Entrez IDs
  entrez_ids <- unlist(strsplit(genes, "/"))
  exprs_degs <- as.data.frame(exprs_degs)
  # Extract logFC values from exprs (column V1)
  logFC_values <- exprs_degs[entrez_ids, "V1"]
  
  # Compute the mean logFC for the pathway
  mean(logFC_values, na.rm = TRUE)
})
  pathway_results <- pairwise_termsim(pathway_results)
  #barplot(pathway_results, showCategory = 20)
  png(paste0("./PATHWAYS/", ident_2, "_vs_", ident_1, "_dotplot_REACTOME.png"), width = 10, height = 15, res = 300, units = "in" )
  p <- dotplot(pathway_results, showCategory = 20)
  print(p)
  dev.off()
  png(paste0("./PATHWAYS/", ident_2, "_vs_", ident_1, "_emapplot_REACTOME.png"), width = 10, height = 15, res = 300, units = "in" )
  p <- emapplot(pathway_results, showCategory = 20)
  print(p)
  dev.off()
  #emapplot(pathway_results, showCategory = 20, color = "logFC")  # Use logFC for node colors

}
```






```{r}
library(clusterProfiler)
library(org.Mm.eg.db)  # Mouse-specific annotation database


# Perform GO enrichment analysis
go_results <- enrichGO(
  gene          = rownames(exprs_degs),  # Use Entrez IDs as input genes
  OrgDb         = org.Mm.eg.db,          # Organism database for mouse
  keyType       = "ENTREZID",            # Specify the type of gene ID
  ont           = "BP",                  # Ontology type: BP, CC, or MF
  pAdjustMethod = "BH",                  # Adjust p-values using Benjamini-Hochberg
  pvalueCutoff  = 0.05,                  # Significance threshold for p-values
  qvalueCutoff  = 0.2,                   # Significance threshold for q-values
  readable      = TRUE                   # Converts Entrez IDs to gene symbols
)

# View the enrichment results
head(as.data.frame(go_results))

barplot(go_results, showCategory = 10, title = "Top 10 Enriched GO Biological Processes")

go_results@result



```







                       
 # ENRICH RESULT
 
```{r}
# Assuming your DEG list is called "deg_genes" and your reference list is called "reference_genes"
library(clusterProfiler)

# Example using enrichGO function
enrich_result <- enrichGO(
    gene          = mouse_data$X,        # Your DEG list
    OrgDb         = org.Mm.eg.db,     # Organism database (e.g., human genes)
    keyType       = "SYMBOL",         # Type of gene identifier (e.g., SYMBOL, ENSEMBL)
    ont           = "BP",             # Ontology type: BP, MF, or CC
    pAdjustMethod = "BH",             # p-value adjustment method
    universe      = rownames(RNA_SPHK1),  # Custom reference list
    pvalueCutoff  = 0.05,
    qvalueCutoff  = 0.2
)
# View the enrichment results
head(as.data.frame(enrich_result))

barplot(enrich_result, showCategory = 10, title = "Top 10 Enriched GO Biological Processes")

```                      
                       
    

#Gaining ENRICHGO RESULTS AUTOMATICALLY PER PAIR

```{r}

ident_pairs <- list(
c("WT_Hypoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "WT_Hypoxia"),
c("SPHK1_Normoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "SPHK1_Normoxia"),
c("WT_Normoxia", "WT_Hypoxia"),
c("WT_Hypoxia", "SPHK1_Hypoxia"),
c("WT_Normoxia", "SPHK1_Normoxia"),
c("SPHK1_Normoxia", "SPHK1_Hypoxia")
)
        # Loop through each pair and find markers
for (pair in ident_pairs) {
  # Extract ident.1 and ident.2 from the pair
  ident_1 <- pair[1]
  ident_2 <- pair[2]
  library(Seurat)
  degs <- FindMarkers(RNA_SPHK1, ident.1 = ident_2, ident.2 = ident_1, assay = "RNA", group.by = "group")
  significant_degs <- degs[degs$p_val_adj < 0.05 & (degs$pct.1 > 0.1 | degs$pct.2 > 0.1),  ]
  library(org.Mm.eg.db)
  entrez_ids <- mapIds(org.Mm.eg.db,
                     keys = rownames(significant_degs),
                     column = "ENTREZID",
                     keytype = "SYMBOL",
                     multiVals = "first")
  names(entrez_ids) <- rownames(significant_degs)
  entrez_valid <- entrez_ids[!is.na(entrez_ids)]
  significant_degs <- significant_degs[names(entrez_valid), ]
  exprs_degs <- matrix(significant_degs$avg_log2FC, ncol = 1)
  rownames(exprs_degs) <- entrez_valid
  
  library(clusterProfiler)
  library(org.Mm.eg.db)  # Mouse-specific annotation database
  # Perform GO enrichment analysis
  go_results <- enrichGO(
  gene          = rownames(exprs_degs),  # Use Entrez IDs as input genes
  OrgDb         = org.Mm.eg.db,          # Organism database for mouse
  keyType       = "ENTREZID",            # Specify the type of gene ID
  ont           = "BP",                  # Ontology type: BP, CC, or MF
  pAdjustMethod = "BH",                  # Adjust p-values using Benjamini-Hochberg
  pvalueCutoff  = 0.05,                  # Significance threshold for p-values
  qvalueCutoff  = 0.2,                   # Significance threshold for q-values
  readable      = TRUE                   # Converts Entrez IDs to gene symbols
)
  write.csv(go_results@result, paste0("./PATHWAYS/", ident_2, "_vs_", ident_1, " enrichGo_results.csv"))
}
   
```
#KEGG RESULTS FOR PATHVIEW!!!

```{r}
kegg_result <- enrichKEGG(gene = rownames(exprs_degs),
                          organism = 'mmu',  # 'hsa' for Homo sapiens (change if necessary)
                          pvalueCutoff = 0.05)
head(kegg_result)

kegg_result_df <- as.data.frame(kegg_result)
#significant_results <- kegg_result_df[kegg_result_df$qvalue < 0.05, ]


#mmu05171

```




#AUTOMATIC KEGG RESULTS DF AND SAVING

```{r}

ident_pairs <- list(
c("WT_Hypoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "WT_Hypoxia"),
c("SPHK1_Normoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "SPHK1_Normoxia"),
c("WT_Normoxia", "WT_Hypoxia"),
c("WT_Hypoxia", "SPHK1_Hypoxia"),
c("WT_Normoxia", "SPHK1_Normoxia"),
c("SPHK1_Normoxia", "SPHK1_Hypoxia")
)
        # Loop through each pair and find markers
for (pair in ident_pairs) {
  # Extract ident.1 and ident.2 from the pair
  ident_1 <- pair[1]
  ident_2 <- pair[2]
  library(Seurat)
  degs <- FindMarkers(RNA_SPHK1, ident.1 = ident_2, ident.2 = ident_1, assay = "RNA", group.by = "group")
  significant_degs <- degs[degs$p_val_adj < 0.05 & (degs$pct.1 > 0.1 | degs$pct.2 > 0.1),  ]
  library(org.Mm.eg.db)
  entrez_ids <- mapIds(org.Mm.eg.db,
                     keys = rownames(significant_degs),
                     column = "ENTREZID",
                     keytype = "SYMBOL",
                     multiVals = "first")
  names(entrez_ids) <- rownames(significant_degs)
  entrez_valid <- entrez_ids[!is.na(entrez_ids)]
  significant_degs <- significant_degs[names(entrez_valid), ]
  exprs_degs <- matrix(significant_degs$avg_log2FC, ncol = 1)
  rownames(exprs_degs) <- entrez_valid
  kegg_result <- enrichKEGG(gene = rownames(exprs_degs),
                          organism = 'mmu',  # 'hsa' for Homo sapiens (change if necessary)
                          pvalueCutoff = 0.05)
  kegg_result_df <- as.data.frame(kegg_result)
  #significant_results <- kegg_result_df[kegg_result_df$qvalue < 0.05, ]
  write.csv(go_results@result, paste0("./PATHWAYS/", ident_2, "_vs_", ident_1, " enrichKEGG_results.csv"))
}
   
```


#PATHVIEW

```{r}
library(pathview)
pv.out <- pathview(gene.data = exprs_degs,
                   pathway.id = "mmu05171",
                   species = "mmu",
                   out.suffix = "WT_hypoxia_vs_WT_Normoxia",
                   kegg.native = TRUE)


pv.out <- pathview(gene.data = exprs_degs,
                   pathway.id = "mmu05171",
                   species = "mmu",
                   out.suffix = "WT_hypoxia_vs_WT_Normoxia",
                   kegg.native = FALSE)
```











#KEGG PATHWAYS

```{r}

data("kegg.sets.mm")
#data("sigmet.idx.rn")
#kegg.sets.rn = kegg.sets.rn[sigmet.idx.rn]
kegg.sets.mm = kegg.sets.mm

```





# HOW TO CHECK THE DATA IN SPECIFIC PACKAGE AND CALL IT

```{r}
data()

data(package = "gage")

data(package = .packages(all.available = TRUE))

data("kegg_category", package = "clusterProfiler")


Data sets in package clusterProfiler:

DE_GSE8057                    Datasets gcSample contains a sample of gene clusters.
gcSample                      Datasets gcSample contains a sample of gene clusters.
kegg_category                 Datasets gcSample contains a sample of gene clusters.
kegg_species                  Datasets gcSample contains a sample of gene clusters.

length(unique(kegg_category$name))

rm(list = ls())
       
```



```{r}
library(KEGGREST)
# List all mouse pathways
mouse_pathways <- keggList("pathway", "mmu")
# Search for inflammation-related pathways
grep("inflammation|immune|cytokine|toll-like", mouse_pathways, value = TRUE)
grep("inflammation|toll|cytokine", mouse_pathways, value = TRUE)

df <- as.data.frame(mouse_pathways)


df$mouse_pathways <- sub(" - Mus musculus \\(house mouse\\)", "", df$mouse_pathways)

write.csv(df, "Keggrest_updated_pathways_mmu.csv")



```





```{r}
library(readxl)
library(AnnotationDbi)
library(org.Mm.eg.db)

# Add Entrez IDs to the original data
mouse_data$ENTREZID <- entrez_ids

# Extract fold changes and name them with Entrez IDs
foldchanges <- mouse_data$avg_log2FC
names(foldchanges) <- mouse_data$ENTREZID


keggres = gage(exprs = foldchanges, gsets = kegg.sets.mm, same.dir = FALSE)



# Check how many genes were mapped successfully
summary(is.na(mouse_data$ENTREZID))
#fold change value
summary(foldchanges)
# Count how many genes are used in pathway analysis
length(intersect(names(foldchanges), unlist(kegg.sets.mm)))

View(keggres$less)

write.csv(keggres$greater, "./gcapb_kegg_true.csv")



#EXTRACT GENES


# Check the gene set associated with the first pathway (Metabolic pathways, mo01100)
genes_in_metabolic_pathway <- kegg.sets.mm[["rno01100 Metabolic pathways"]]
metabolic_gcapb <- intersect(genes_in_metabolic_pathway, gcapb$ENTREZID)
class(metabolic_gcapb)
metabolic_gcapb <- as.data.frame(metabolic_gcapb)

metabolic_gcapb$gene_symbols <- NA
metabolic_gcapb$log_fold <- NA

matching_indices <- match(metabolic_gcapb$metabolic_gcapb, gcapb$ENTREZID)

metabolic_gcapb$log_fold <-  gcapb$gCapB.avg_log2FC[matching_indices]

# View the genes
print(genes_in_metabolic_pathway)


write.csv(metabolic_gcapb, "./metabolic_pathway_genes.csv")

```















#UMAPs

```{r, fig.height=19, fig.width=19}

#PERI SMOOTH
png("Pericyte_SMC_per_group.png", width = 19, height = 5, units = "in", res = 300)
DimPlot(sphk1_perismc, group.by = "Parse_StromAnn2", split.by = "group", pt.size = 2) + ggtitle("Pericytes and Smooth Muscle Cells")
dev.off()

png("Pericyte_SMC_all_together.png", width = 7, height = 5, units = "in", res = 300)
DimPlot(sphk1_perismc, group.by = "Parse_StromAnn2",  pt.size = 2, label = T) + NoLegend() + ggtitle("Pericytes and Smooth Muscle Cells")
dev.off()


DimPlot(sphk1_perismc, group.by = "Parse_StromAnn2", split.by = "group", pt.size = 2)
getwd()




png("Endothelial_cells_per_group.png", width = 19, height = 5, units = "in", res = 300)
DimPlot(Endo_SPHK1, group.by = "annot1", split.by = "group", pt.size = 1) + ggtitle("Endothelial Cells")
dev.off()

png("Endothelial_cells_all_groups_together.png", width = 7, height = 5, units = "in", res = 300)
DimPlot(Endo_SPHK1, group.by = "annot1",  pt.size = 1, label = T) + NoLegend() + ggtitle("Endothelial Cells")
dev.off()


DimPlot(RNA_SPHK1, group.by = "Parse_StromAnn", split.by = "group", pt.size = 2)
getwd()


library(Seurat)
DimPlot(RNA_SPHK1, group.by = "Parse_Ann1",  pt.size = 1, label = T) + NoLegend() + ggtitle("Whole Lung")


png("Whole_lung_all_groups_together.png", width = 13, height = 15, units = "in", res = 300)
DimPlot(RNA_SPHK1, group.by = "Parse_Ann1",  pt.size = 1, label = T, repel = T) + NoLegend() + ggtitle("Whole_Lung")
dev.off()



png("Whole_lung_per_group.png", width = 30, height = 15, units = "in", res = 300)
DimPlot(RNA_SPHK1, group.by = "Parse_Ann1",  pt.size = 1, label = T, repel = T, split.by = "group") + NoLegend() + ggtitle("Whole_Lung")
dev.off()


RNA_SPHK1$Parse_Ann1 <-RNA_SPHK1$Parse_Ann 
RNA_SPHK1$Parse_Ann1[RNA_SPHK1$Parse_Ann1 %in% "AT1"] <- "Mesothelial cells"
RNA_SPHK1$Parse_Ann1[RNA_SPHK1$Parse_Ann1 %in% c("gCapB", "gCapA", "gCapC", "gCapD", "gCapE")] <- "gCaps"
RNA_SPHK1$Parse_Ann1[RNA_SPHK1$Parse_Ann1 %in% c("Vascular Smc", "Airway Smc")] <- "Smooth muscle cells"
RNA_SPHK1$Parse_Ann1[RNA_SPHK1$Parse_Ann1 %in% "Aerocyte II"] <- "gCaps"
RNA_SPHK1$Parse_Ann1[sub] <- "Aerocyte I"
RNA_SPHK1$Parse_Ann1[RNA_SPHK1$Parse_Ann1 %in% "Aerocyte I"] <- "aCaps"
RNA_SPHK1$Parse_Ann2 <-RNA_SPHK1$Parse_Ann1

RNA_SPHK1$Parse_Ann1[RNA_SPHK1$Parse_Ann1 %in% c("Vascular Smc", "Airway Smc")] <- "Smooth muscle cells"
RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann1 %in% c("Peribronchial fibroblasts", "Alveolar fibroblasts", "Adventitial fibroblasts", "Myofibroblasts")] <- "Fibroblasts"
RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann1 %in% c("Monocyte-derived Macrophages", "Interstitial Macrophages")] <- "Macrophages"

RNA_SPHK1$Parse_Ann2 <- gsub(" proliferating$", "", RNA_SPHK1$Parse_Ann2)
# Remove "Prolif. " from the beginning of cell names in the Parse_Ann2 column
RNA_SPHK1$Parse_Ann2 <- gsub("^Prolif\\. ", "", RNA_SPHK1$Parse_Ann2)

RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann2 %in% c("Act. Alveolar M", "Alveolar M")] <- "Alveolar Macrophages"

RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann1 %in% c("Cd8+ NK cells", "Immature Cd8+ NK cells")] <- "NK cells"
RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann2 %in% c("DC1", "DC2", "Plasmacytoid DCs")] <- "Dendritic cells"
RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann1 %in% c("aCaps", "gCaps", "PAECs", "PVECs", "Lymphatic EC")] <- "Endothelial cells"

RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann2 %in% c("Th1 cells", "Th17 cells", "CD8+ T Cells", "Helper T Cells", "Tregs")] <- "T cells"
RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann1 %in% c("AT1")] <- "Alveolar type I cell"
RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann1 %in% c("AT2")] <- "Alveolar type II cell"
RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann1 %in% c("Transitional Pericytes")] <- "Smooth muscle cells"
RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann2 %in% c("Brush cells")] <- "Alveolar Macrophages"
RNA_SPHK1$Parse_Ann2[RNA_SPHK1$seurat_clusters %in% 6] <- "Alveolar Macrophages"
RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann2 %in% c("Mast cells")] <- NA
RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann2 %in% c("Plasma cells")] <- NA
RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann2 %in% c("Macrophages")] <- "Interstititonal Macrophages"
RNA_SPHK1$Parse_Ann2[RNA_SPHK1$Parse_Ann2 %in% c("Interstititonal Macrophages")] <- "Interstitial Macrophages"


DimPlot(RNA_SPHK1, group.by = "Parse_Ann2",  pt.size = 1, label = T) + NoLegend() + ggtitle("Whole Lung")


sub <- subset(RNA_SPHK1, umap_2 < -7 & umap_1 > 8)
sub <- colnames(sub)
DimPlot(sub)
table(RNA_SPHK1$Parse_Ann2)


#Alveolar Macrophage Cd68, Mertk, Itgax(cd11c), siglec1
#interstitial Macrophage Adgr1, Itgam, (mrc1), Cd163, Cd14
Macrophages <- Cd68, Mertk, Adgre1(F4/80)
Macrophages <- c("Cd68", "Mertk", "Adgre1", "Marco", "Itgax", "Itgam", "Siglec1", "RT1-Da", "Mrc1", "Cd163", "Ccr2")   #Adgre1(F4/80) #RT1-Da-HLA_DRA

FeaturePlot(RNA_SPHK1, Neutrophil_markers)
Neutrophil_markers <- c("S100a9", "S100a8", "Cxcr2", "Prtn3", "Sell", "Elane", "Il1b", "Stfa2", "Stfa2l1")


SCT_SPHK1$Parse_Ann2 <- NA

SCT_SPHK1$Parse_Ann2 <- RNA_SPHK1$Parse_Ann2


DimPlot(RNA_SPHK1, label = T)

DimPlot(RNA_SPHK1, group.by = "Parse_Ann2",  pt.size = 1, label = T, repel = T) + NoLegend() + ggtitle("Whole Lung")

DimPlot(RNA_SPHK1, cells.highlight = colnames(SCT_SPHK1)[SCT_SPHK1$Parse_Ann2 %in% "Neutrophils"]) + NoLegend() + ggtitle("Whole Lung")



DimPlot(RNA_SPHK1, group.by = "Parse_Ann2",  pt.size = 1, label = T, repel = T) + NoLegend() + ggtitle("Whole Lung")
FeaturePlot(RNA_SPHK1, "Mki67")
```


# MAKING TABLE FOR NEW

```{r}
# MAKING THE TABLE

RNA_SPHK1$group1 <- RNA_SPHK1$group1
table(RNA_SPHK1$group1)
df <- as.data.frame(table(RNA_SPHK1$Parse_Ann2))

df1 <- as.data.frame(table(RNA_SPHK1$Parse_Ann2[RNA_SPHK1$group1 == "WT_Normoxia"]))
df2 <- as.data.frame(table(RNA_SPHK1$Parse_Ann2[RNA_SPHK1$group1 == "WT_Hypoxia"]))
df3 <-as.data.frame(table(RNA_SPHK1$Parse_Ann2[RNA_SPHK1$group1 == "SPHK1_Normoxia"]))
df4 <-as.data.frame(table(RNA_SPHK1$Parse_Ann2[RNA_SPHK1$group1 == "SPHK1_Hypoxia"]))

rownames(df) <- df$Var1

rownames(df1) <- df1$Var1
rownames(df2) <- df2$Var1
rownames(df3) <- df3$Var1 %>% 
rownames(df4) <- df4$Var1

df$Var1 <- NULL
df1$Var1 <- NULL
df2$Var1 <- NULL
df3$Var1 <- NULL
df4$Var1 <- NULL

colnames(df)[1] <- "All_groups"
colnames(df1)[1] <- "WT Normoxia"
colnames(df2)[1] <- "WT Hypoxia"
colnames(df3)[1] <- "SPHK1 Normoxia"
colnames(df4)[1] <- "SPHK1 Hypoxia"





# Match rownames of df to rownames of df1
matched_indices <- match(rownames(df), rownames(df1))
df$WT_Normoxia<- NA
df$WT_Normoxia<- 0
df$WT_Normoxia[!is.na(matched_indices)] <- df1[matched_indices[!is.na(matched_indices)], "WT Normoxia"]

matched_indices <- match(rownames(df), rownames(df2))
df$WT_Hypoxia<- NA
df$WT_Hypoxia<- 0
df$WT_Hypoxia[!is.na(matched_indices)] <- df2[matched_indices[!is.na(matched_indices)], "WT Hypoxia"]

matched_indices <- match(rownames(df), rownames(df3))
df$SPHK1_Normoxia<- NA
df$SPHK1_Normoxia<- 0
df$SPHK1_Normoxia[!is.na(matched_indices)] <- df3[matched_indices[!is.na(matched_indices)], "SPHK1 Normoxia"]

matched_indices <- match(rownames(df), rownames(df4))
df$SPHK1_Hypoxia<- NA
df$SPHK1_Hypoxia<- 0
df$SPHK1_Hypoxia[!is.na(matched_indices)] <- df4[matched_indices[!is.na(matched_indices)], "SPHK1 Hypoxia"]

df <- df[!rownames(df) %in% "AT1", ]
df <- df[!rownames(df) %in% "Basal Epithelial", ]

# ILLUSTRATING DF TABLE

# Load necessary libraries
library(ggplot2)
library(tidyr)

df$Cell_Type <- rownames(df)

# Convert data frame to long format
df_long <- pivot_longer(df, cols = c("WT_Normoxia", "WT_Hypoxia", "SPHK1_Normoxia", "SPHK1_Hypoxia"),
                        names_to = "Condition", values_to = "Count")


library(gridExtra)
library(ggplot2) 
# Open a PNG device to save the output as a high-resolution image (300 dpi)
png("Parse_Ann2_percentages.png", width = 15, height = 19, units = "in", res = 300) #7

# Arrange and save all plots in a grid with 3 columns
p

# Close the graphics device
dev.off()



# Create grouped bar plot
p <- ggplot(df_long, aes(x = Cell_Type, y = Count, fill = Condition)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = Count), 
          position = position_stack(vjust = 0.5), # Position the text labels in the middle of each bar section
          size = 3, color = "black") +
  labs(x = "Cell Type", y = "Count", title = "Comparison of Counts by Condition for Each Cell Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_brewer(palette = "Set1") #+
  #scale_y_continuous(limits = c(0, 2500))


table(Endo_SPHK1$orig.ident)
table(RNA_SPHK1$orig.ident)

table(df$WT_Normoxia)

#PERCENTAGES OF DF
df$WT_Normoxia_per <- NA
df$WT_Normoxia_per <- (df$WT_Normoxia * 100) / 9211


df$WT_Hypoxia_per <- NA
df$WT_Hypoxia_per <- (df$WT_Hypoxia * 100) / 8603

df$SPHK1_Normoxia_per <- NA
df$SPHK1_Normoxia_per <- (df$SPHK1_Normoxia * 100) / 7427

df$SPHK1_Hypoxia_per <- NA
df$SPHK1_Hypoxia_per <- (df$SPHK1_Hypoxia * 100) / 7674

write.csv(df, "Parse_Ann2_df.csv")


#df$total <- NULL
#df$total[df_long$Condition == "WT_Normoxia"] <- 9211
#df$total[df_long$Condition == "WT_Hypoxia"] <- 8604
#df$total[df_long$Condition == "SPHK1_Normoxia"] <- 7427
#df$total[df_long$Condition == "SPHK1_Hypoxia"] <- 7674



df_long$total <- NA
df_long$total[df_long$Condition == "WT_Normoxia"] <- 9211
df_long$total[df_long$Condition == "WT_Hypoxia"] <- 8603
df_long$total[df_long$Condition == "SPHK1_Normoxia"] <- 7427
df_long$total[df_long$Condition == "SPHK1_Hypoxia"] <- 7674


df_long$count_percent <- NA
df_long$count_percent <- (df_long$Count * 100) / df_long$total


table(RNA_SPHK1$orig.ident)

sum(df$SPHK1_Hypoxia)

# Create grouped bar plot
p <- ggplot(df_long, aes(x = Cell_Type, y = count_percent, fill = Condition)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = sprintf("%.1f", count_percent)), 
          position = position_stack(vjust = 0.5), # Position the text labels in the middle of each bar section
          size = 3, color = "black") +
  labs(x = "Cell Type", y = "count_percentage", title = "Comparison of Percentages by Condition for Whole Lung Cell Types") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_brewer(palette = "Set1")

getwd()

yes <- rownames(RNA_SPHK1)[grep("Stat", rownames(RNA_SPHK1))]
class(yes)


for(i in yes){
  p <- DotPlot(RNA_SPHK1, i, group.by = "group", scale.min = 0) + coord_flip() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  print(p)
}

for(i in genes){
  p <- DotPlot(RNA_SPHK1, i, group.by = "group", scale.min = 0) + coord_flip() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  print(p)
}

colSums(df[, sapply(df, is.numeric)])
```

#MAKING TABLE FOR EC SUBTYPES

```{r}

# MAKING THE TABLE

Endo_SPHK1$group1 <- RNA_SPHK1$group1
table(Endo_SPHK1$group1)
df <- as.data.frame(table(Endo_SPHK1$annot1))

df1 <- as.data.frame(table(Endo_SPHK1$annot1[Endo_SPHK1$group1 == "WT_Normoxia"]))
df2 <- as.data.frame(table(Endo_SPHK1$annot1[Endo_SPHK1$group1 == "WT_Hypoxia"]))
df3 <-as.data.frame(table(Endo_SPHK1$annot1[Endo_SPHK1$group1 == "SPHK1_Normoxia"]))
df4 <-as.data.frame(table(Endo_SPHK1$annot1[Endo_SPHK1$group1 == "SPHK1_Hypoxia"]))

rownames(df) <- df$Var1

rownames(df1) <- df1$Var1
rownames(df2) <- df2$Var1
rownames(df3) <- df3$Var1
rownames(df4) <- df4$Var1

df$Var1 <- NULL
df1$Var1 <- NULL
df2$Var1 <- NULL
df3$Var1 <- NULL
df4$Var1 <- NULL

colnames(df)[1] <- "All_groups"
colnames(df1)[1] <- "WT Normoxia"
colnames(df2)[1] <- "WT Hypoxia"
colnames(df3)[1] <- "SPHK1 Normoxia"
colnames(df4)[1] <- "SPHK1 Hypoxia"





# Match rownames of df to rownames of df1
matched_indices <- match(rownames(df), rownames(df1))
df$WT_Normoxia<- NA
df$WT_Normoxia<- 0
df$WT_Normoxia[!is.na(matched_indices)] <- df1[matched_indices[!is.na(matched_indices)], "WT Normoxia"]

matched_indices <- match(rownames(df), rownames(df2))
df$WT_Hypoxia<- NA
df$WT_Hypoxia<- 0
df$WT_Hypoxia[!is.na(matched_indices)] <- df2[matched_indices[!is.na(matched_indices)], "WT Hypoxia"]

matched_indices <- match(rownames(df), rownames(df3))
df$SPHK1_Normoxia<- NA
df$SPHK1_Normoxia<- 0
df$SPHK1_Normoxia[!is.na(matched_indices)] <- df3[matched_indices[!is.na(matched_indices)], "SPHK1 Normoxia"]

matched_indices <- match(rownames(df), rownames(df4))
df$SPHK1_Hypoxia<- NA
df$SPHK1_Hypoxia<- 0
df$SPHK1_Hypoxia[!is.na(matched_indices)] <- df4[matched_indices[!is.na(matched_indices)], "SPHK1 Hypoxia"]


# ILLUSTRATING DF TABLE

# Load necessary libraries
library(ggplot2)
library(tidyr)

df$Cell_Type <- rownames(df)

# Convert data frame to long format
df_long <- pivot_longer(df, cols = c("WT_Normoxia", "WT_Hypoxia", "SPHK1_Normoxia", "SPHK1_Hypoxia"),
                        names_to = "Condition", values_to = "Count")



colSums(df[, sapply(df, is.numeric)])


# Create grouped bar plot
p <- ggplot(df_long, aes(x = Cell_Type, y = Count, fill = Condition)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = Count), 
          position = position_stack(vjust = 0.5), # Position the text labels in the middle of each bar section
          size = 3, color = "black") +
  labs(x = "Cell Type", y = "Count", title = "Comparison of Counts by Condition for Each EC Subpopulations") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_brewer(palette = "Set1") #+
  #scale_y_continuous(limits = c(0, 2500))


table(Endo_SPHK1$orig.ident)
table(RNA_SPHK1$orig.ident)

table(df$WT_Normoxia)

#PERCENTAGES OF DF
df$WT_Normoxia_per <- NA
df$WT_Normoxia_per <- (df$WT_Normoxia * 100) / 2730


df$WT_Hypoxia_per <- NA
df$WT_Hypoxia_per <- (df$WT_Hypoxia * 100) / 1673

df$SPHK1_Normoxia_per <- NA
df$SPHK1_Normoxia_per <- (df$SPHK1_Normoxia * 100) / 2306

df$SPHK1_Hypoxia_per <- NA
df$SPHK1_Hypoxia_per <- (df$SPHK1_Hypoxia * 100) / 2577

write.csv(df, "Endothelial_df.csv")


df_long$total <- NA
df_long$total[df_long$Condition == "WT_Normoxia"] <- 2730
df_long$total[df_long$Condition == "WT_Hypoxia"] <- 1673
df_long$total[df_long$Condition == "SPHK1_Normoxia"] <- 2306
df_long$total[df_long$Condition == "SPHK1_Hypoxia"] <- 2577


df_long$count_percent <- NA
df_long$count_percent <- (df_long$Count * 100) / df_long$total



# Create grouped bar plot
p <- ggplot(df_long, aes(x = Cell_Type, y = count_percent, fill = Condition)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = sprintf("%.1f", count_percent)), 
          position = position_stack(vjust = 0.5), # Position the text labels in the middle of each bar section
          size = 3, color = "black") +
  labs(x = "Cell Type", y = "count_percent", title = "Comparison of count_percentages by Condition for Each EC Subpopulations") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_brewer(palette = "Set1")




library(gridExtra)
library(ggplot2) 
# Open a PNG device to save the output as a high-resolution image (300 dpi)
png("Endothelial_subpopulations_counts.png", width = 10, height = 15, units = "in", res = 300) #7

# Arrange and save all plots in a grid with 3 columns
p

# Close the graphics device
dev.off()
```


#----------------------------------------------------------------------
#----------------------------------------------------------------------
#----------------------------------------------------------------------
#----------------------------------------------------------------------
#----------------------------------------------------------------------
#Gaining ENRICHGO RESULTS PRE SUBGROUPS of EC cells

```{r}
Ec_subs <- table(Endo_SPHK1$annot1)
Ec_subs <- names(Ec_subs)

for (i in Ec_subs){

  subcluster <- subset(Endo_SPHK1, annot1 == i)
  
ident_pairs <- list(
c("WT_Hypoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "WT_Hypoxia"),
c("SPHK1_Normoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "SPHK1_Normoxia"),
c("WT_Normoxia", "WT_Hypoxia"),
c("WT_Hypoxia", "SPHK1_Hypoxia"),
c("WT_Normoxia", "SPHK1_Normoxia"),
c("SPHK1_Normoxia", "SPHK1_Hypoxia")
)
        # Loop through each pair and find markers
for (pair in ident_pairs) {
  # Extract ident.1 and ident.2 from the pair
  ident_1 <- pair[1]
  ident_2 <- pair[2]
  library(Seurat)
  degs <- FindMarkers(subcluster, ident.1 = ident_2, ident.2 = ident_1, assay = "RNA", group.by = "group")
  significant_degs <- degs[degs$p_val_adj < 0.05 & (degs$pct.1 > 0.1 | degs$pct.2 > 0.1),  ]
  library(org.Mm.eg.db)
  entrez_ids <- mapIds(org.Mm.eg.db,
                     keys = rownames(significant_degs),
                     column = "ENTREZID",
                     keytype = "SYMBOL",
                     multiVals = "first")
  names(entrez_ids) <- rownames(significant_degs)
  entrez_valid <- entrez_ids[!is.na(entrez_ids)]
  significant_degs <- significant_degs[names(entrez_valid), ]
  exprs_degs <- matrix(significant_degs$avg_log2FC, ncol = 1)
  rownames(exprs_degs) <- entrez_valid
  
  library(clusterProfiler)
  library(org.Mm.eg.db)  # Mouse-specific annotation database
  # Perform GO enrichment analysis
  go_results <- enrichGO(
  gene          = rownames(exprs_degs),  # Use Entrez IDs as input genes
  OrgDb         = org.Mm.eg.db,          # Organism database for mouse
  keyType       = "ENTREZID",            # Specify the type of gene ID
  ont           = "BP",                  # Ontology type: BP, CC, or MF
  pAdjustMethod = "BH",                  # Adjust p-values using Benjamini-Hochberg
  pvalueCutoff  = 0.05,                  # Significance threshold for p-values
  qvalueCutoff  = 0.2,                   # Significance threshold for q-values
  readable      = TRUE                   # Converts Entrez IDs to gene symbols
)
  write.csv(go_results@result, paste0("./PATHWAYS_new/", i, "_", ident_2, "_vs_", ident_1, " enrichGo_results.csv"))
}
}


   
```


#Gaining ENRICHGO RESULTS of SMC/pericytes and fibroblasts

```{r}
Sphk1_subs <- table(RNA_SPHK1$Parse_Ann2)
Sphk1_subs <- names(Sphk1_subs)
Sphk1_subs <-Sphk1_subs[c(10,17,18)] 


for (i in Sphk1_subs){

  subcluster <- subset(RNA_SPHK1, Parse_Ann2 == i)
  
ident_pairs <- list(
c("WT_Hypoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "WT_Hypoxia"),
c("SPHK1_Normoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "SPHK1_Normoxia"),
c("WT_Normoxia", "WT_Hypoxia"),
c("WT_Hypoxia", "SPHK1_Hypoxia"),
c("WT_Normoxia", "SPHK1_Normoxia"),
c("SPHK1_Normoxia", "SPHK1_Hypoxia")
)
        # Loop through each pair and find markers
for (pair in ident_pairs) {
  # Extract ident.1 and ident.2 from the pair
  ident_1 <- pair[1]
  ident_2 <- pair[2]
  library(Seurat)
  degs <- FindMarkers(subcluster, ident.1 = ident_2, ident.2 = ident_1, assay = "RNA", group.by = "group")
  significant_degs <- degs[degs$p_val_adj < 0.05 & (degs$pct.1 > 0.1 | degs$pct.2 > 0.1),  ]
  library(org.Mm.eg.db)
  entrez_ids <- mapIds(org.Mm.eg.db,
                     keys = rownames(significant_degs),
                     column = "ENTREZID",
                     keytype = "SYMBOL",
                     multiVals = "first")
  names(entrez_ids) <- rownames(significant_degs)
  entrez_valid <- entrez_ids[!is.na(entrez_ids)]
  significant_degs <- significant_degs[names(entrez_valid), ]
  exprs_degs <- matrix(significant_degs$avg_log2FC, ncol = 1)
  rownames(exprs_degs) <- entrez_valid
  
  library(clusterProfiler)
  library(org.Mm.eg.db)  # Mouse-specific annotation database
  # Perform GO enrichment analysis
  go_results <- enrichGO(
  gene          = rownames(exprs_degs),  # Use Entrez IDs as input genes
  OrgDb         = org.Mm.eg.db,          # Organism database for mouse
  keyType       = "ENTREZID",            # Specify the type of gene ID
  ont           = "BP",                  # Ontology type: BP, CC, or MF
  pAdjustMethod = "BH",                  # Adjust p-values using Benjamini-Hochberg
  pvalueCutoff  = 0.05,                  # Significance threshold for p-values
  qvalueCutoff  = 0.2,                   # Significance threshold for q-values
  readable      = TRUE                   # Converts Entrez IDs to gene symbols
)
  write.csv(go_results@result, paste0("./PATHWAYS_new/", i, "_", ident_2, "_vs_", ident_1, " enrichGo_results.csv"))
}
}


   
```

#REACTOME ANALYSIS for EC cells


```{r, fig.height=4, fig.width=10}

Ec_subs <- table(Endo_SPHK1$annot1)
Ec_subs <- names(Ec_subs)

for (i in Ec_subs){

  subcluster <- subset(Endo_SPHK1, annot1 == i)
  
  
ident_pairs <- list(
c("WT_Hypoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "WT_Hypoxia"),
c("SPHK1_Normoxia", "WT_Normoxia"),
c("SPHK1_Hypoxia", "SPHK1_Normoxia"),
c("WT_Normoxia", "WT_Hypoxia"),
c("WT_Hypoxia", "SPHK1_Hypoxia"),
c("WT_Normoxia", "SPHK1_Normoxia"),
c("SPHK1_Normoxia", "SPHK1_Hypoxia")
)
        # Loop through each pair and find markers
for (pair in ident_pairs) {
  # Extract ident.1 and ident.2 from the pair
  ident_1 <- pair[1]
  ident_2 <- pair[2]
  library(Seurat)
  degs <- FindMarkers(subcluster, ident.1 = ident_2, ident.2 = ident_1, assay = "RNA", group.by = "group")
  significant_degs <- degs[degs$p_val_adj < 0.05 & (degs$pct.1 > 0.1 | degs$pct.2 > 0.1),  ]
  library(org.Mm.eg.db)
  entrez_ids <- mapIds(org.Mm.eg.db,
                     keys = rownames(significant_degs),
                     column = "ENTREZID",
                     keytype = "SYMBOL",
                     multiVals = "first")
  names(entrez_ids) <- rownames(significant_degs)
  entrez_valid <- entrez_ids[!is.na(entrez_ids)]
  significant_degs <- significant_degs[names(entrez_valid), ]
  exprs_degs <- matrix(significant_degs$avg_log2FC, ncol = 1)
  rownames(exprs_degs) <- entrez_valid
  
  library(ReactomePA)
  library(enrichplot)
  pathway_results <- enrichPathway(gene = rownames(exprs_degs), organism = "mouse", pvalueCutoff = 0.05)
  #ADDING LOG VALUES TO PATHWAY ANALYSIS
  pathway_results@result$logFC <- sapply(pathway_results@result$geneID, function(genes) {
  # Split geneID into individual Entrez IDs
  entrez_ids <- unlist(strsplit(genes, "/"))
  exprs_degs <- as.data.frame(exprs_degs)
  # Extract logFC values from exprs (column V1)
  logFC_values <- exprs_degs[entrez_ids, "V1"]
  
  # Compute the mean logFC for the pathway
  mean(logFC_values, na.rm = TRUE)
})
  pathway_results <- pairwise_termsim(pathway_results)
  #barplot(pathway_results, showCategory = 20)
  png(paste0("./PATHWAYS_new/reactome", i, "_", ident_2, "_vs_", ident_1, "_dotplot_REACTOME.png"), width = 10, height = 15, res = 300, units = "in" )
  p <- dotplot(pathway_results, showCategory = 20)
  print(p)
  dev.off()
  png(paste0("./PATHWAYS_new/reactome", i, "_", ident_2, "_vs_", ident_1, "_emapplot_REACTOME.png"), width = 10, height = 15, res = 300, units = "in" )
  p <- emapplot(pathway_results, showCategory = 20)
  print(p)
  dev.off()
  #emapplot(pathway_results, showCategory = 20, color = "logFC")  # Use logFC for node colors

}
}

```


```{r}

Ec_subs <- table(Endo_SPHK1$annot1)
Ec_subs <- names(Ec_subs)
Ec_subs <- Ec_subs[4]

for (i in Ec_subs){

  subcluster <- subset(Endo_SPHK1, annot1 == i)
  
  
ident_pairs <- list(
#c("WT_Hypoxia", "WT_Normoxia")#,
#c("SPHK1_Hypoxia", "WT_Hypoxia")#, c("SPHK1_Normoxia", "WT_Normoxia")#, c("SPHK1_Hypoxia", "SPHK1_Normoxia")#, c("WT_Normoxia", "SPHK1_Normoxia")#, c("SPHK1_Normoxia", "SPHK1_Hypoxia")#, c("WT_Hypoxia", "SPHK1_Hypoxia")#,c("WT_Normoxia", "WT_Hypoxia")
)
        # Loop through each pair and find markers
for (pair in ident_pairs) {
  # Extract ident.1 and ident.2 from the pair
  write.csv(pair, "pair_current.csv")
  ident_1 <- pair[1]
  ident_2 <- pair[2]
  library(Seurat)
  degs <- FindMarkers(subcluster, ident.1 = ident_2, ident.2 = ident_1, assay = "RNA", group.by = "group")
  significant_degs <- degs[degs$p_val_adj < 0.05 & (degs$pct.1 > 0.1 | degs$pct.2 > 0.1),  ]
  library(org.Mm.eg.db)
  entrez_ids <- mapIds(org.Mm.eg.db,
                     keys = rownames(significant_degs),
                     column = "ENTREZID",
                     keytype = "SYMBOL",
                     multiVals = "first")
  names(entrez_ids) <- rownames(significant_degs)
  entrez_valid <- entrez_ids[!is.na(entrez_ids)]
  significant_degs <- significant_degs[names(entrez_valid), ]
  exprs_degs <- matrix(significant_degs$avg_log2FC, ncol = 1)
  rownames(exprs_degs) <- entrez_valid
  
  library(ReactomePA)
  library(enrichplot)
  pathway_results <- enrichPathway(gene = rownames(exprs_degs), organism = "mouse", pvalueCutoff = 0.05)

  #ADDING LOG VALUES TO PATHWAY ANALYSIS
  pathway_results@result$logFC <- sapply(pathway_results@result$geneID, function(genes) {
  # Split geneID into individual Entrez IDs
  entrez_ids <- unlist(strsplit(genes, "/"))
  exprs_degs <- as.data.frame(exprs_degs)
  # Extract logFC values from exprs (column V1)
  logFC_values <- exprs_degs[entrez_ids, "V1"]
  
  # Compute the mean logFC for the pathway
  mean(logFC_values, na.rm = TRUE)
})
  pathway_results <- pairwise_termsim(pathway_results)
        # Skip the rest if pairwise_termsim fails to calculate meaningful results
 
  #barplot(pathway_results, showCategory = 20)
  png(paste0("./PATHWAYS_new/reactome", i, "_", ident_2, "_vs_", ident_1, "_dotplot_REACTOME.png"), width = 10, height = 15, res = 300, units = "in" )
  p <- dotplot(pathway_results, showCategory = 20)
  print(p)
  dev.off()
  png(paste0("./PATHWAYS_new/reactome", i, "_", ident_2, "_vs_", ident_1, "_emapplot_REACTOME.png"), width = 10, height = 15, res = 300, units = "in" )
  p <- emapplot(pathway_results, showCategory = 20)
  print(p)
  dev.off()
  #emapplot(pathway_results, showCategory = 20, color = "logFC")  # Use logFC for node colors

}
}

```

# percyte and smooth REACTOME
```{r}
Sphk1_subs <- table(RNA_SPHK1$Parse_Ann2)
Sphk1_subs <- names(Sphk1_subs)
Sphk1_subs <-Sphk1_subs[c(10,17,18)] 
Sphk1_subs <-Sphk1_subs[2] 


for (i in Sphk1_subs){

  subcluster <- subset(RNA_SPHK1, Parse_Ann2 == i)
  
  
ident_pairs <- list(
#c("WT_Hypoxia", "WT_Normoxia"),
#c("SPHK1_Hypoxia", "WT_Hypoxia"),
#c("SPHK1_Normoxia", "WT_Normoxia"),
#c("SPHK1_Hypoxia", "SPHK1_Normoxia"),
#c("WT_Normoxia", "WT_Hypoxia"),
#c("WT_Hypoxia", "SPHK1_Hypoxia"),
c("WT_Normoxia", "SPHK1_Normoxia"),
c("SPHK1_Normoxia", "SPHK1_Hypoxia")
)
        # Loop through each pair and find markers
for (pair in ident_pairs) {
  # Extract ident.1 and ident.2 from the pair
  ident_1 <- pair[1]
  ident_2 <- pair[2]
  library(Seurat)
  degs <- FindMarkers(subcluster, ident.1 = ident_2, ident.2 = ident_1, assay = "RNA", group.by = "group")
  significant_degs <- degs[degs$p_val_adj < 0.05 & (degs$pct.1 > 0.1 | degs$pct.2 > 0.1),  ]
  library(org.Mm.eg.db)
  entrez_ids <- mapIds(org.Mm.eg.db,
                     keys = rownames(significant_degs),
                     column = "ENTREZID",
                     keytype = "SYMBOL",
                     multiVals = "first")
  names(entrez_ids) <- rownames(significant_degs)
  entrez_valid <- entrez_ids[!is.na(entrez_ids)]
  significant_degs <- significant_degs[names(entrez_valid), ]
  exprs_degs <- matrix(significant_degs$avg_log2FC, ncol = 1)
  rownames(exprs_degs) <- entrez_valid
  
  library(ReactomePA)
  library(enrichplot)
  pathway_results <- enrichPathway(gene = rownames(exprs_degs), organism = "mouse", pvalueCutoff = 0.05)
  #ADDING LOG VALUES TO PATHWAY ANALYSIS
  pathway_results@result$logFC <- sapply(pathway_results@result$geneID, function(genes) {
  # Split geneID into individual Entrez IDs
  entrez_ids <- unlist(strsplit(genes, "/"))
  exprs_degs <- as.data.frame(exprs_degs)
  # Extract logFC values from exprs (column V1)
  logFC_values <- exprs_degs[entrez_ids, "V1"]
  
  # Compute the mean logFC for the pathway
  mean(logFC_values, na.rm = TRUE)
})
  pathway_results <- pairwise_termsim(pathway_results)
  #barplot(pathway_results, showCategory = 20)
  png(paste0("./PATHWAYS_new/reactome", i, "_", ident_2, "_vs_", ident_1, "_dotplot_REACTOME.png"), width = 10, height = 15, res = 300, units = "in" )
  p <- dotplot(pathway_results, showCategory = 20)
  print(p)
  dev.off()
  png(paste0("./PATHWAYS_new/reactome", i, "_", ident_2, "_vs_", ident_1, "_emapplot_REACTOME.png"), width = 10, height = 15, res = 300, units = "in" )
  p <- emapplot(pathway_results, showCategory = 20)
  print(p)
  dev.off()
  #emapplot(pathway_results, showCategory = 20, color = "logFC")  # Use logFC for node colors

}
}

```
```{r, fig.height=10}
DimPlot(RNA_SPHK1, group.by = "Parse_Ann1", label = T) +NoLegend()
DimPlot(Stroma_SPHK1, group.by = "Parse_Ann", label = T) + NoLegend()

Stroma_SPHK1$parse

FeaturePlot(RNA_SPHK1, "Acta2")
FeaturePlot(RNA_SPHK1, "Acta2")
c("Acta2", "Myh11", "Cnn1", "Tagln")

FeaturePlot(Stroma_SPHK1, c("Acta2", "Myh11", "Cnn1", "Tagln"))

```




```{r, fig.height=10, fig.width=15}
SCMF_markers <- c("Agt", "Pdgfra", "Egfem1", "Htra1", "Tnc", "P2ry14", "Tgfbi", "Ltbp2", "Spon2")
SCMF_gpt <- c("Acta2", "Myh11", "Cnn1", "Col1a1", "Col3a1", "Pdgfra", "Fap", "Tagln", "Tpm2", "Sparc")
Pericyte_cell_card <- c("Lamc3", "Trpc6", "Cspg4", "Pdgfrb")
Myofibroblasts_gpt <- c("Acta2", "Tagln", "Myh11", "Tpm2", "Col1a1", "Col3a1", "Fn1", "Tnc", "Tgfb1", "Pdgfra", "Vcl", "Paxillin", "Des", "Vim", "Postn", "Spp1", "Thbs1")
Vascular_smo <- c("Map3k7cl","Aoc3", "Ntrk3","Gpc6")
Pnec <- c("Calca", "Grp", "Ascl1", "Scg5", "Cxc13", "Ngf", "Scg2", "Nov", 
           "Chgb", "Uchl1", "Pkib", "Ddc", "Snap25", "Pcsk1", "Snca", "Bex2", 
           "Dnajc12")


PMP <- c("Adh1", "Hoxb5", "Slc38a5", "Snai2", "Col13a1", "Ccnb1")
DimPlot(RNA_SPHK1, group.by = "Parse_Ann1", label = T, repel = T) + NoLegend()

for(i in PMP){
    if(i %in% rownames(RNA_SPHK1)){
  p <- FeaturePlot(RNA_SPHK1, i, order = T, raster = F)
  print(p)
    }else {message(paste("Gene", i, "is", "missing", sep = " "))
    }
}


DimPlot(RNA_SPHK1, group.by = "Parse_Ann1", split.by = "orig.ident", cells.highlight = colnames(RNA_SPHK1)[grep("Myo", RNA_SPHK1$Parse_Ann1)], raster = F)



Marker <- FindMarkers(RNA_SPHK1, group.by = "Parse_Ann1", ident.1 = "Pericytes", only.pos = T, min.pct = 0.25, logfc.threshold = 0.25)
library(dplyr)
Marker <- Marker %>% 
  filter(p_val_adj < 0.5) %>%
  top_n(n =33, wt = avg_log2FC) #%>% 
  #filter(pct.1 > 0.700)#%>%
  #filter(pct.1 - pct.2 > 0.400)



Marker <- FindMarkers(RNA_SPHK1, ident.1 = 21, only.pos = T, min.pct = 0.25, logfc.threshold = 0.25)
library(dplyr)
Marker <- Marker %>% 
  filter(p_val_adj < 0.5) %>%
  top_n(n =33, wt = avg_log2FC) #%>% 
  #filter(pct.1 > 0.700)#%>%
  #filter(pct.1 - pct.2 > 0.400)


FeaturePlot(RNA_SPHK1, "Acta2", order = T, raster = F, split.by = "orig.ident")


DimPlot(RNA_SPHK1, label = T, repel = T) + NoLegend()


```


```{r}

for (i in 1:4){
  anchors <- FindTransferAnchors(
  reference = Parsall_comb,         # Reference Seurat object (with known T cell labels)
  query = RNA_SPHK1_list[[i]],                 # Query Seurat object (to which we want to transfer labels)
  normalization.method = "LogNormalize",       # Normalization method (use "SCT" if you did SCTransform or "SCT")
  reference.assay = "RNA",            # Assay in the reference Seurat object (usually "RNA" for raw or normalized counts)
  query.assay = "RNA",                # Assay in the query Seurat object
  dims = 1:30                         # Number of dimensions to use for anchor identification
)
  #2- Second Tranfer labels
  Bis_Wlwl_Sugen_Elh <- TransferData(anchorset = anchors,
                             refdata = Parsall_comb$Annotation_transfer_EC,
                             dims = 1:30
                             )
  RNA_SPHK1_list[[i]]$Annotation_transfer_EC <- Bis_Wlwl_Sugen_Elh$predicted.id
  
  Bis_Wlwl_Sugen_Elh <- TransferData(anchorset = anchors,
                             refdata = Parsall_comb$Marker_Ann,
                             dims = 1:30
                             )
  RNA_SPHK1_list[[i]]$Marker_Ann <- Bis_Wlwl_Sugen_Elh$predicted.id
  
}

#MERGE ALL 4
merged_seurat <- Reduce(function(x, y) merge(x, y), RNA_SPHK1_list)
RNA_SPHK1$Annotation_transfer_EC <- NA
RNA_SPHK1$Marker_Ann <- NA
RNA_SPHK1$Annotation_transfer_EC<- merged_seurat$Annotation_transfer_EC
RNA_SPHK1$Marker_Ann <- merged_seurat$Marker_Ann

```

